### 2020-10-07 IUI2021/paper.tex
論文関連追加

%%

% \documentclass[manuscript,anonymous,review]{acmart}
\documentclass[manuscript,screen,review]{acmart}

\long\def\comment#1{}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Beyond query expansion - expanding documents for fluid keyword search}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Toshiyuki Masui}
\email{masui@pitecan.com}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Keio University}
  \streetaddress{1234 Endo}
  \city{Fujisawa}
  \state{Kanagawa}
  \country{Japan}
  \postcode{43017-6221}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Toshiyuki Masui}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Although intelligent text search algorithms are widely available
  these days, documents are still hard to find in many cases. It is
  usually hard to find useful information in help systems and manual
  pages, even when required information exists in the documents.

  Searches fail mainly because of the ``vocabulary problem,'' where users
  cannot find the right search keyword. When a user wants to
  ``remove a file,''and there is a manual entry or ``deleting a file,'' users may
  not be able to know how to remove a file until he finds the right
  keyword ``delete'' for the search.
  To solve the problem, various \textit{query expansion}
  techniques are widely used on the Web. When a user
  types ``remove'' in the search box, the system automatically expands the
  keyword and suggests using ``remove/delete'' instead. Query expansion
  works effectively for simple cases, but it does not work well when the
  concept in the users' mind is very different from the text in the
  manual document. For example, if a user wants to ``clean up the
  desktop,'' he cannot find an appropriate manual entry that only
  describes how to ``delete icons'' or ``align icons'' on the desktop.

  We propose a new approach \textit{document expansion} for finding
  help documents and manual entries. We provide flexible explanations
  for each document using regular expression patterns. For the above
  example, we give an expression like \texttt{(delete|remove) (a file|data)}
  and use the expanded text like \texttt{delete a file}, \texttt{remove data} for
  keyword search. Also, a pattern like \texttt{(delete|remove) \#{file}} is
  expanded to \texttt{delete Makefile}, \texttt{delete search.c}, etc. depending on
  the existing files, so that a user can enter \texttt{del ma} to get
  \texttt{delete Makefile} and immediately execute it.

  We have been using this document expansion technique called
  ExpandSearch for several years, and the system is working on various
  commercial Web services. In this paper, we describe the idea and
  implementation of ExpandHelp and show how it works in the wild.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}

% \endinput

### 2020-10-07 IUI2021/paper.tex
...

@@
 \documentclass[manuscript,screen,review]{acmart}
+
+\usepackage{here} % [H]とするとその場所に配置されるらしい
 
@@
 
+% 異なる言語でも大丈夫
+% Translation paradigm
+
 %%
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{text search, help systems, query expansion}
 
@@
 
-\section{Research Methods}
+People are frequently searching information using keywords on Google
+and other systems, but keyword search is still not an easy task,
+because it is fundamentally difficulto to find appropriate information
+that does not contain the keyword given by the user.
 
-\subsection{Part One}
+\begin{verbatim}
+Webでもパソコンでも情報検索はキーワード検索が主流だが、キーワード検索は昔も今も難しい
+根本的に、[[本文に含まれていない文字列の検索が難しい]]からである
+\end{verbatim}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
+On the help system of MacOS Catalina (v10.15.5), we cannot tell how to remove a file
 
-\subsection{Part Two}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=10cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
+  \caption{Mac}
+  \Description{Mac Mac}
+\end{figure}
 
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
+We can find how to set the clock, but the user has to know that
+setting the clock and changing date is the same thing.
 
-\section{Online Resources}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=10cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
+  \caption{Mac}
+  \Description{Mac Mac}
+\end{figure}
 
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
+We can find information on Google because...
+For example we can find how to XXXX by using YYYY, because somebody on the net has written an article on XXXX using the keyword YYYY.
 
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
+\begin{verbatim}
+Googleとかで意外とみつかる気がするのは、Web上のメジャーな情報は
+いろんな人がいろんな言葉で情報をアップしてるからだろう (出典)
+機能を検索したとき、トップに出るのはメーカーのサイトではない
+情報が無いからではなく、キーワードがマッチしないからだと思われる
+\end{verbatim}
+
+We can find the information on XXXX because XXXX is fairly popular, but finding information of less popular things is more difficult.
+
+\begin{verbatim}
+メジャーじゃないシステムや特殊な状況のヘルプなどの場合、文書もユーザも少ないから苦労する
+キーワードが少しでも違うとみつからない
+開発者の用語とユーザの用語が違うことの違いの問題がさらにひどい
+\end{verbatim}
+
+When we want to find the user's console of Google Chrome extension, we
+cannot find it on Google search, because the official name of the
+feature is "Google dashboard."
+
+\begin{verbatim}
+e.g. メジャーじゃないxxxxxシステムのyyyyy機能
+  Google Chrome Extensionのconsoleとかみつからない (dashboardだとみつかる)
+		(他の例も)
+\end{verbatim}
+
+FAQs provided by service providers are not usually considered useful
+because the terms used by the people on the service are usually
+different from the word that user can think of.
+
+\begin{verbatim}
+いわゆるFAQは大抵不十分(出典)
+   特殊なサービスの特殊な機能について書かれてることが多いからだろう
+   メジャーなサービスであっても、ググって本家FAQが出てくることなど無い
+    誰かが言い替えたものがヒットするのが普通 (出典)
+\end{verbatim}
+
+Even finding the users' old documents can be sometimes difficult,
+because people might want to use different keywords for the same
+thing. He might try to find a file on "ZZZ" and fail, because he used
+the term "WWW" instead before.
+
+\begin{verbatim}
+自分のメモですら後でみつけられなくて困ることも多い
+ 微妙に利用単語が違うとみつからない
+ 良いファイル名をつけたつもりでも後から検索できないことがある
+\end{verbatim}
+
+Various techniques have been proposed to solve this vocabulary problem.
+But not very successful.
+
+\begin{verbatim}
+母語が違うときはさらに大変である
+頭の中の単語を英語に変換する必要がある
+常にTranslationや言い替えが必要だといっていいだろう
+(いったん文書がみつかれば、それを理解することはできるが、そもそもみつけるのが難しいのである)
+クエリや検索技術を工夫して解決しようとする方法が多い
+原文はいじれないから
+ いろんな言い回しで検索する研究は大昔からある
+\end{verbatim}
+
+If the system knows that removing a file and deleting a file is the same, the system can try to find something using the keyword "delete", even when the user specified the keyword "remove".
+
+\begin{verbatim}
+シソーラスを使うことがすぐ考えられる
+\end{verbatim}
+
+This kind of technique is called [/* Query expansion], and simle query
+expansion is possible if proper dictionary is provided.
+
+\subsection{Query Expansion}
+
+\begin{verbatim}
+クエリに工夫する方法
+   シソーラス的検索の一般化
+   検索対象の本文は変わらないから不十分
+   クエリだけ拡張してもしょうがない
+   本文に固有名詞的なものが少ない場合はみつけにくい
+   e.g. 「良い論文を書く方法」「査読を通す方法」「インパクトある論文を書く方法」
+    「レビュワーを説得する技術」 vs 「良い論文を書く方法」
+ユーザが指定するあらゆるキーワードを拡張するのは不可能である
+John F. Kennedy
+
+翻訳してから検索するのも一種のQUery Expansionである
+日本語を入力すると英語のWikipediaがみつかることもある => これは違う原理
+\end{verbatim}
+
+Query expansion is effective when simple substitution of keywords are satisfactory enough.
+Using 'delete' in addition to 'remove' works...
+However, it does not work for finding a document for vague topics.
+For example, if you want to find a document that describes "how to write a good paper",
+you will have little chance finding a document related to the topic.
+Maybe it would be better to use keywords like "how to persuade reviewers".
+However, expanding a phrase like "write a good paper" to "persude reviewers" is impossible.
+
+\begin{verbatim}
+  別の言い替え文書(Tipsとか逆引き辞典)を用意
+   便利だがメジャーなものに限られる
+   もと文書と全然違うところで作り直しは大変すぎるが、逆引き本は売れている
+   hands-on と言うのだろうか?
+    ちょっと違う
+    handbook かな?
+    firsthand
+\end{verbatim}
+
+Similarly, 
+When we want to find a library function of a programming language, query expansion does not work.
+For example, when we want to write a poker game and want to select five cards from the deck,
+what library should we use?
+you want to selet randomly two items from an array in Ruby,
+you can use the `sample()` method.
+However, "randomly selecting items" and "sample" are so different, it is very hard for users to
+find the method unless the manual contains words like "randomly select"
+
+\begin{verbatim}
+「配列からランダムに要素をふたつ取得」 = `a.sample(2)`
+    `sample`という単語はなかなか出てこないのではないか
+    pick upとかselectとかchooseとか言ってしまいそう
+\end{verbatim}
+
+It is even more difficult if the user wants to find information that is not easily described with keywords.
+When a user wants to know what the icons on the Mac desktop mean, he might want to to 
+search by saying "What is the symbol with three curved lines [wifi.icon] on my computer display?
+(folding fan, two black 90-degree arcs above a black circcle)
+
+\begin{verbatim}
+  特殊な言葉が使われていない場合は検索が難しい
+   「Macの画面の上の方の宇宙船みたいな記号」では駄目
+    「メニューバーの音声アイコン」だとみつかるかもしれないが
+  他の言語の場合でも同じである
+ [[原文を拡張する感じにして、簡潔なインタフェースを用意して任意のキーワードを使えるのが良い]]
+\end{verbatim}
+
+There should be better way to make everything more searchable by casual computer users.
+
+\section{Solutions}
+
+\begin{verbatim}
+[[解決策]]
+ [[解決策1:]] 展開ヘルプで徹底的に拡張/曖昧検索
+  [[検索対象側で、いろんなクエリに対応できるような工夫をしておく]]
+  あらゆるクエリにマッチするように、いろんな表現を用意しておく
+   Query をExpandするわけではなく、あらゆるQueryに対応できるように[[本文をExpandする]]
+   本文になければ、いくらQueryをExpandしてもみつからないから
+   クエリパタンで`(dashboard|console)` などと指定するのではなく、[[本文に両方書いておく]]
+   RegExpによる展開とAsearchによる曖昧検索
+  いろんな表現を用意しておけばいろんな表現で検索できるのはあたりまえだが、用意する手間は減らせる
+ [[解決策2:]] ユーザが勝手に検索対象をExpandする
+  逆引き辞典式
+  既存のキーワード検索インタフェースをユーザが拡張する
+  自分で登録 (scrapbox, 拡張機能)
+   `console`でも検索できるようにする
+  自分のデータには記述するし、他人のデータにも記述する
+ これらを[[ExpandSearch]]と呼ぶ
+  フツーの検索システムの上に皮をかぶせる形で実装する
+\end{verbatim}
+
+To solve the vocabulary problem, we propose the combination of three techniques.
+
+\begin{itemize}
+
+\item Using ExpandSearch
+
+The main idea for solving the problem is 
+providing \textbf{regular expressions} (REs)
+for  each document so that a wide variety of user queries can match one of the expanded strings.
+
+When we want to provide a manual that describes how to delete a file, 
+we provide a RE like \verb|(delete|remove) (a file|data)|
+and generate all the text that match this RE.
+In this case, we can epand this RE into
+\verb|delete a file|,
+\verb|delete data|,
+\verb|remove a file|, and
+\verb|remove data|.
+and use all these strings for the search.
+Users can find this document by using fleible query like
+\verb|delete file| or
+\verb|remove data|.
+We can add descriptions in other languages, like \verb|(ファイル|データ)を(消す|(消去|削除)する)|
+A user can use a phrase like ``ファイルを消去する'' to find the manual page.
+
+\item Approximate pattern matching
+
+People make spelling errors all the time, and approximate pattern matching algorithm works quite effectively for almost all search activities.
+Using the ExpandHelp algorithm, all the expressions are expanded in advance,
+so simple approximate pattern matching algorithms can be applied for the search.
+For example, a query like ``del dta'' can be used
+
+\item Document expansion by users
+
+As we have shown before, one of the big reasons why we fail to find a document is that
+the user's search keyword does not exist in the document.
+ Providing entries for ExpandHelp can solve the problem, but
+If the author of the does not provide the data, it would be nice if other users can add
+the ExpandHelp entries.
+This strategy is very similar to writing a hands-on document for an existing document,
+but adding ExpandHelp entries is much easier than authoring  a document from scratch.
+
+\end{itemize}
+
+\section{Examples}
+
+\subsection{Helpfeel services}
+
+We have been applying ExpahdSearch for various customer support services on existing Web services.
+The help system based on ExpandSearch is called \textit{Helpfeel}, and
+
+Helpfeel is a FAQ engine that supports users who do not have enough vocabulary for the Web services they want to use.
+
+\begin{verbatim}
+(ここでどこかのサポートシステムを示す)
+\end{verbatim}
+
+Figure xxx shows an example Helpfeel page that supports finding FAQs
+for PayPay Free market run by Yahoo! Japan.
+We provide the description on the Scrapbox wiki service,
+
+\begin{verbatim}
+ https://paypayfleamarket.yahoo.co.jp/help/
+[https://gyazo.com/3d964512606a5e25646104a738ab104e]
+\end{verbatim}
+
+\subsection{HelpLine}
+
+Some Unix command line tools have many options and features, and difficult to understand in many cases.
+Many programmers are recently using the git version control system, but the concept of git is difficult, and
+the command line options are extremely complicated.
+The total number of git manuals on unix is .....
+
+We created the GitHelp system using ExpandHelp, so that git users can easily
+remember command options and use it without perfectly remembering the git commands.
+
+\subsection{OmniHelp}
+
+OmniHelp is an implementation of ExpandHelp that runs on Chrome browser.
+The URL window on Chrome is called omnibox,
+
+\begin{verbatim}
+[[ExpandSearchの実例]]
+ まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
+[[実例1]] ExpandHelpの実際の利用
+ ScrapboxというWiki上にいろんな表現を用意しておく
+ Helpfeel
+  PayPayフリマなどですごく効率があがった
+ 実際これによりヘルプ問い合わせは劇的に減る (出典: Helpfeel)
+[[実例2]] 検索インタフェースの融合
+ マイHelpfeel
+ 検索をひとつの方法に統合する
+  検索方法が複数だと面倒臭い
+   ググって出なければ逆引き辞典を検索する、みたいなのは面倒
+  同じ検索インタフェースでいろんなところを探すほうが簡単である
+  どこにメモしたか忘れて困ることがなくなる
+ 自分のデータが増えていく状況のグラフを書ける!
+
+[[実例3]]
+ gitのヘルプ - コマンドラインで動くもの
+  パラメタを指定して実行につなげることすらできる
+\end{verbatim}
+
+\section{Implementation}
+
+\begin{verbatim}
+[[実装]]
+ ExpandHelpのアルゴリズム
+  正規表現の拡張とパラメタ代入
+ HelpLineの実装
+  omniboxを利用するとか
+\end{verbatim}
+
+\section{Discussions}
+
+\begin{verbatim}
+    検索システムを選んでから検索キーワードを入力するのに慣れてしまっている
+  この必要がないことを知ると驚きがある
+ 検索されやすいように工夫するとか馬鹿げてると
+思うかもしれないか、ググって出なきゃ無いのと同じだということを考えると、
+ある程度工夫することは意味があるし、自分が後でさがすときにも役に立つわけである
+  ゲームのように記述を増やす工夫もできるかもしれない
+  タイトルに迷ったら両方書くみたいな
+ どこにある情報でもひとつのインタフェースでみつかるのは強烈に嬉しい
+
+[[説得ポイント]]
+ ExpandHelp
+  自分が入力したキーワードが検索結果に出現する嬉しさ
+ 検索方法の統合
+ ヘルプシステムの実績
+
+[[関連システム / 参考文献]]
+ 普通の[https://en.wikipedia.org/wiki/Query_expansion クエリ拡張]
+ Relevance Feedback
+  検索パタンを増やすことに効果があるといえる
+ [https://scrapbox.io/UIPedia/George_Furnas:_The_vocabulary_problem_in_human-system_communication Vocabulary problem]
+ [文芸的プログラミング]
+  ExpandHelp記述は文芸的プログラミングの一種だと思えばいい
+  冗長な感じで書くといい
+ [/Rubytips] の実例
+
+日本語を入力すると英語のWikipediaがみつかることもある
+ これはたぶん原文を翻訳したものを検索対象にしている
+ これもDocument Expansionといえる
+
+\end{verbatim}
 

### 2020-10-07 IUI2021/paper.tex
...

@@
 
-\begin{verbatim}
-Webでもパソコンでも情報検索はキーワード検索が主流だが、キーワード検索は昔も今も難しい
-根本的に、[[本文に含まれていない文字列の検索が難しい]]からである
-\end{verbatim}
+% Webでもパソコンでも情報検索はキーワード検索が主流だが、キーワード検索は昔も今も難しい
+% 根本的に、[[本文に含まれていない文字列の検索が難しい]]からである
 
-On the help system of MacOS Catalina (v10.15.5), we cannot tell how to remove a file
+The help system of MacOS (Catalina v10.15.5) does not tell a user how to remove a file.
 
@@
   \includegraphics[width=10cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
-  \caption{Mac}
+  \caption{Asking the help application how to remove a file.}
   \Description{Mac Mac}
@@
 
-We can find how to set the clock, but the user has to know that
-setting the clock and changing date is the same thing.
+Using the same help application, 
+a user can find how to set the system clock of the computer,
+but the user has to know that
+``setting the clock'' and ``changing date'' means the same thing.
 
@@
 
-We can find information on Google because...
-For example we can find how to XXXX by using YYYY, because somebody on the net has written an article on XXXX using the keyword YYYY.
+We can get this kind of information fairly easily using search systems on Internet,
+so many people prefer getting information using search engines rather than
+using help systems provided by manufacturers.
 
-\begin{verbatim}
-Googleとかで意外とみつかる気がするのは、Web上のメジャーな情報は
-いろんな人がいろんな言葉で情報をアップしてるからだろう (出典)
-機能を検索したとき、トップに出るのはメーカーのサイトではない
-情報が無いからではなく、キーワードがマッチしないからだと思われる
-\end{verbatim}
+We can find information on Google because there are tremendous information
+that describe how to ``remove a file'' on Mac.
+If there are documens that contain ``remove'', ``file'', and ``Mac'',
+finding such documents are not easy.
 
-We can find the information on XXXX because XXXX is fairly popular, but finding information of less popular things is more difficult.
+That seems to be the main reason why people are satisfied with search engines on the net
+for finding popular? information.
 
-\begin{verbatim}
-メジャーじゃないシステムや特殊な状況のヘルプなどの場合、文書もユーザも少ないから苦労する
-キーワードが少しでも違うとみつからない
-開発者の用語とユーザの用語が違うことの違いの問題がさらにひどい
-\end{verbatim}
+% For example we can find how to XXXX by using YYYY, because somebody on the net has written an article on XXXX using the keyword YYYY.
 
-When we want to find the user's console of Google Chrome extension, we
-cannot find it on Google search, because the official name of the
-feature is "Google dashboard."
+% Googleとかで意外とみつかる気がするのは、Web上のメジャーな情報は
+% いろんな人がいろんな言葉で情報をアップしてるからだろう (出典)
+% 機能を検索したとき、トップに出るのはメーカーのサイトではない
+% 情報が無いからではなく、キーワードがマッチしないからだと思われる
 
-\begin{verbatim}
-e.g. メジャーじゃないxxxxxシステムのyyyyy機能
-  Google Chrome Extensionのconsoleとかみつからない (dashboardだとみつかる)
-		(他の例も)
-\end{verbatim}
+On the other hand,
+finding a less popular information is rather difficult,
+because not enough document related to the topic is found on the net.
+
+If there is only one document on the net
+that describes the \texttt{console} feature of a minor system \texttt{xxxxx},
+people cannot find the document using a similar keyword \texttt{dashboard}
+since the document does not contain the word \texttt{dashboard}.
+
+% メジャーじゃないシステムや特殊な状況のヘルプなどの場合、文書もユーザも少ないから苦労する
+% キーワードが少しでも違うとみつからない
+% 開発者の用語とユーザの用語が違うことの違いの問題がさらにひどい
+
+% e.g. メジャーじゃないxxxxxシステムのyyyyy機能
+%   Google Chrome Extensionのconsoleとかみつからない (dashboardだとみつかる)
+% 	(他の例も)
 
@@
 
-\begin{verbatim}
-いわゆるFAQは大抵不十分(出典)
-   特殊なサービスの特殊な機能について書かれてることが多いからだろう
-   メジャーなサービスであっても、ググって本家FAQが出てくることなど無い
-    誰かが言い替えたものがヒットするのが普通 (出典)
-\end{verbatim}
+% いわゆるFAQは大抵不十分(出典)
+%   特殊なサービスの特殊な機能について書かれてることが多いからだろう
+%   メジャーなサービスであっても、ググって本家FAQが出てくることなど無い
+%    誰かが言い替えたものがヒットするのが普通 (出典)
 
 Even finding the users' old documents can be sometimes difficult,
-because people might want to use different keywords for the same
+because people might use different keywords for the same
 thing. He might try to find a file on "ZZZ" and fail, because he used
-the term "WWW" instead before.
+the term "WWW" before.
 
-\begin{verbatim}
-自分のメモですら後でみつけられなくて困ることも多い
- 微妙に利用単語が違うとみつからない
- 良いファイル名をつけたつもりでも後から検索できないことがある
-\end{verbatim}
+% 自分のメモですら後でみつけられなくて困ることも多い
+%  微妙に利用単語が違うとみつからない
+%  良いファイル名をつけたつもりでも後から検索できないことがある
 
@@
 
-\begin{verbatim}
-母語が違うときはさらに大変である
-頭の中の単語を英語に変換する必要がある
-常にTranslationや言い替えが必要だといっていいだろう
-(いったん文書がみつかれば、それを理解することはできるが、そもそもみつけるのが難しいのである)
-クエリや検索技術を工夫して解決しようとする方法が多い
-原文はいじれないから
- いろんな言い回しで検索する研究は大昔からある
-\end{verbatim}
+Finding documents are even more difficult when
+the user's mother language is different from the language used in the document.
+When a user wants to find how to ``delete a file'' but the
+manual of the system is written in French,
+he has to \textbf{translate} the term ``delete'' and ``file''
+before the search.
+Non-English speakers are always having trouble
+translating the word in their brain into English words
+before searching on the net.
 
-If the system knows that removing a file and deleting a file is the same, the system can try to find something using the keyword "delete", even when the user specified the keyword "remove".
-
-\begin{verbatim}
-シソーラスを使うことがすぐ考えられる
-\end{verbatim}
-
-This kind of technique is called [/* Query expansion], and simle query
-expansion is possible if proper dictionary is provided.
+% 母語が違うときはさらに大変である
+% 頭の中の単語を英語に変換する必要がある
+% 常にTranslationや言い替えが必要だといっていいだろう
+% (いったん文書がみつかれば、それを理解することはできるが、そもそもみつけるのが難しいのである)
+% クエリや検索技術を工夫して解決しようとする方法が多い
+% 原文はいじれないから
+%  いろんな言い回しで検索する研究は大昔からある
 
@@
 
-\begin{verbatim}
-クエリに工夫する方法
-   シソーラス的検索の一般化
-   検索対象の本文は変わらないから不十分
-   クエリだけ拡張してもしょうがない
-   本文に固有名詞的なものが少ない場合はみつけにくい
-   e.g. 「良い論文を書く方法」「査読を通す方法」「インパクトある論文を書く方法」
-    「レビュワーを説得する技術」 vs 「良い論文を書く方法」
-ユーザが指定するあらゆるキーワードを拡張するのは不可能である
-John F. Kennedy
+The vocabulary problem and the translation problem can be solved
+if the search system have a thesaurus and a translation dictionary.
 
-翻訳してから検索するのも一種のQUery Expansionである
-日本語を入力すると英語のWikipediaがみつかることもある => これは違う原理
-\end{verbatim}
+For example, 
+if the system knows that removing a file and deleting a file is the same,
+the system can try to find something using the keyword ``delete'',
+even when the user specified the keyword ``remove''.
+
+This kind of technique is called \textit{Query expansion}, and simple query
+expansion is possible if proper dictionary is provided.
+
+% クエリに工夫する方法
+%    シソーラス的検索の一般化
+%    検索対象の本文は変わらないから不十分
+%    クエリだけ拡張してもしょうがない
+%    本文に固有名詞的なものが少ない場合はみつけにくい
+%    e.g. 「良い論文を書く方法」「査読を通す方法」「インパクトある論文を書く方法」
+%     「レビュワーを説得する技術」 vs 「良い論文を書く方法」
+% ユーザが指定するあらゆるキーワードを拡張するのは不可能である
+% John F. Kennedy
+% 
+% 翻訳してから検索するのも一種のQUery Expansionである
+% 日本語を入力すると英語のWikipediaがみつかることもある => これは違う原理
 
@@
 Using 'delete' in addition to 'remove' works...
+
 However, it does not work for finding a document for vague topics.
-For example, if you want to find a document that describes "how to write a good paper",
+For example, if you want to find a document that describes ``how to write a good paper'',
 you will have little chance finding a document related to the topic.
-Maybe it would be better to use keywords like "how to persuade reviewers".
-However, expanding a phrase like "write a good paper" to "persude reviewers" is impossible.
+Maybe it would be better to use keywords like ``how to persuade reviewers''.
+However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
+unless the expander knows the contents.
 
-\begin{verbatim}
-  別の言い替え文書(Tipsとか逆引き辞典)を用意
-   便利だがメジャーなものに限られる
-   もと文書と全然違うところで作り直しは大変すぎるが、逆引き本は売れている
-   hands-on と言うのだろうか?
-    ちょっと違う
-    handbook かな?
-    firsthand
-\end{verbatim}
+%  別の言い替え文書(Tipsとか逆引き辞典)を用意
+%   便利だがメジャーなものに限られる
+%   もと文書と全然違うところで作り直しは大変すぎるが、逆引き本は売れている
+%   hands-on と言うのだろうか?
+%    ちょっと違う
+%    handbook かな?
+%    firsthand
 
 Similarly, 
-When we want to find a library function of a programming language, query expansion does not work.
-For example, when we want to write a poker game and want to select five cards from the deck,
-what library should we use?
+when we want to find a library function of a programming language, query expansion does not work.
+For example, when we want to write a poker game program and
+want to select five cards from the deck, what library should we use?
 you want to selet randomly two items from an array in Ruby,
-you can use the `sample()` method.
-However, "randomly selecting items" and "sample" are so different, it is very hard for users to
-find the method unless the manual contains words like "randomly select"
+you can use the \texttt{sample()} method.
+However, ``randomly selecting items'' and \texttt{sample} are so different, it is very hard for users to
+find the method unless the manual contains words like ``randomly select''.
 
-\begin{verbatim}
-「配列からランダムに要素をふたつ取得」 = `a.sample(2)`
-    `sample`という単語はなかなか出てこないのではないか
-    pick upとかselectとかchooseとか言ってしまいそう
-\end{verbatim}
+% 「配列からランダムに要素をふたつ取得」 = `a.sample(2)`
+%    `sample`という単語はなかなか出てこないのではないか
+%    pick upとかselectとかchooseとか言ってしまいそう
 
@@
 When a user wants to know what the icons on the Mac desktop mean, he might want to to 
-search by saying "What is the symbol with three curved lines [wifi.icon] on my computer display?
+search by saying "What is the symbol with three curved lines
+\includegraphics[width=6mm,bb=0 0 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
+on my computer display?
 (folding fan, two black 90-degree arcs above a black circcle)
 
-\begin{verbatim}
-  特殊な言葉が使われていない場合は検索が難しい
-   「Macの画面の上の方の宇宙船みたいな記号」では駄目
-    「メニューバーの音声アイコン」だとみつかるかもしれないが
-  他の言語の場合でも同じである
- [[原文を拡張する感じにして、簡潔なインタフェースを用意して任意のキーワードを使えるのが良い]]
-\end{verbatim}
+%  特殊な言葉が使われていない場合は検索が難しい
+%   「Macの画面の上の方の宇宙船みたいな記号」では駄目
+%    「メニューバーの音声アイコン」だとみつかるかもしれないが
+%  他の言語の場合でも同じである
+% [[原文を拡張する感じにして、簡潔なインタフェースを用意して任意のキーワードを使えるのが良い]]
 
@@
 
-\begin{verbatim}
-[[解決策]]
- [[解決策1:]] 展開ヘルプで徹底的に拡張/曖昧検索
-  [[検索対象側で、いろんなクエリに対応できるような工夫をしておく]]
-  あらゆるクエリにマッチするように、いろんな表現を用意しておく
-   Query をExpandするわけではなく、あらゆるQueryに対応できるように[[本文をExpandする]]
-   本文になければ、いくらQueryをExpandしてもみつからないから
-   クエリパタンで`(dashboard|console)` などと指定するのではなく、[[本文に両方書いておく]]
-   RegExpによる展開とAsearchによる曖昧検索
-  いろんな表現を用意しておけばいろんな表現で検索できるのはあたりまえだが、用意する手間は減らせる
- [[解決策2:]] ユーザが勝手に検索対象をExpandする
-  逆引き辞典式
-  既存のキーワード検索インタフェースをユーザが拡張する
-  自分で登録 (scrapbox, 拡張機能)
-   `console`でも検索できるようにする
-  自分のデータには記述するし、他人のデータにも記述する
- これらを[[ExpandSearch]]と呼ぶ
-  フツーの検索システムの上に皮をかぶせる形で実装する
-\end{verbatim}
+% [[解決策]]
+%  [[解決策1:]] 展開ヘルプで徹底的に拡張/曖昧検索
+%   [[検索対象側で、いろんなクエリに対応できるような工夫をしておく]]
+%   あらゆるクエリにマッチするように、いろんな表現を用意しておく
+%    Query をExpandするわけではなく、あらゆるQueryに対応できるように[[本文をExpandする]]
+%    本文になければ、いくらQueryをExpandしてもみつからないから
+%    クエリパタンで`(dashboard|console)` などと指定するのではなく、[[本文に両方書いておく]]
+%    RegExpによる展開とAsearchによる曖昧検索
+%   いろんな表現を用意しておけばいろんな表現で検索できるのはあたりまえだが、用意する手間は減らせる
+%  [[解決策2:]] ユーザが勝手に検索対象をExpandする
+%   逆引き辞典式
+%   既存のキーワード検索インタフェースをユーザが拡張する
+%   自分で登録 (scrapbox, 拡張機能)
+%    `console`でも検索できるようにする
+%   自分のデータには記述するし、他人のデータにも記述する
+%  これらを[[ExpandSearch]]と呼ぶ
+%   フツーの検索システムの上に皮をかぶせる形で実装する
 
-To solve the vocabulary problem, we propose the combination of three techniques.
+To solve the vocabulary problem and the translation problem,
+we propose the combination of three techniques.
 
@@
 
-\begin{verbatim}
-(ここでどこかのサポートシステムを示す)
-\end{verbatim}
+% ここでどこかのサポートシステムを示す
 

### 2020-10-07 IUI2021/paper.tex
...

@@
 To solve the vocabulary problem and the translation problem,
-we propose the combination of three techniques.
+we propose the combination of three techniques described below.
 
-\begin{itemize}
+\begin{enumerate}
 
-\item Using ExpandSearch
+\item \textbf{Using ExpandSearch}
 
@@
   providing \textbf{regular expressions} (REs)
-for  each document so that a wide variety of user queries can match one of the expanded strings.
+  for  each document so that a wide variety of user queries can match one of the
+  strings expanded from the REs.
 
   When we want to provide a manual that describes how to delete a file, 
-we provide a RE like \verb|(delete|remove) (a file|data)|
+  we provide a RE like \verb*(delete|remove) (a file|data)*
   and generate all the text that match this RE.
@@
   \verb|remove data|.
-We can add descriptions in other languages, like \verb|(ファイル|データ)を(消す|(消去|削除)する)|
+  We can add descriptions in other languages, like \verb*(ファイル|データ)を(消す|(消去|削除)する)*
   A user can use a phrase like ``ファイルを消去する'' to find the manual page.
 
-\item Approximate pattern matching
+\item \textbf{Approximate pattern matching}
 
-People make spelling errors all the time, and approximate pattern matching algorithm works quite effectively for almost all search activities.
+  People make spelling errors all the time, and approximate pattern matching algorithm
+  works quite effectively for almost all search activities.
   Using the ExpandHelp algorithm, all the expressions are expanded in advance,
@@
 
-\item Document expansion by users
+\item \textbf{Document expansion by users}
 
@@
   the user's search keyword does not exist in the document.
- Providing entries for ExpandHelp can solve the problem, but
-If the author of the does not provide the data, it would be nice if other users can add
-the ExpandHelp entries.
+  Providing entries for ExpandSearch can solve the problem, but
+
+  If the author of the document does not provide the data, it would be nice if
+  other users can add the ExpandHelp entries.
   This strategy is very similar to writing a hands-on document for an existing document,
@@
 
-\end{itemize}
+\end{enumerate}
 
@@
 
-\subsection{Helpfeel services}
+\subsection{Helpfeel}
 
@@
 
-\begin{verbatim}
- https://paypayfleamarket.yahoo.co.jp/help/
-[https://gyazo.com/3d964512606a5e25646104a738ab104e]
-\end{verbatim}
+% https://paypayfleamarket.yahoo.co.jp/help/
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
+  \caption{PayPay Freemarket}
+  \Description{PayPay}
+\end{figure}
 

### 2020-10-07 IUI2021/paper.tex
...

@@
 \usepackage{here} % [H]とするとその場所に配置されるらしい
+
+\def\GH{\textsf{GitHelp}}
+\def\GIT{\texttt{git}}
+\def\EH{\textsf{ExpandHelp}}
+\def\SB{\textsf{Scrapbox}}
+\long\def\tt#1{\texttt{#1}}
+\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
+\long\def\sf#1{\textsf{#1}}
+\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
+\long\def\qtt#1{``\tt{#1}''}   % quote tt
+\long\def\sqtt#1{``\stt{#1}''} % small quote tt
+\long\def\qsf#1{``\sf{#1}''}
+\long\def\sqsf#1{``\ssf{#1}''}
+\long\def\qit#1{``\textit{#1}''}
+\long\def\smallfont{\fontsize{9pt}{0pt}\selectfont}
 
@@
 
+----------------------------
+
+We implemented the {\GH} system
+with which a user can translate his vague intention in various languages
+into a complete {\GIT} command
+using the {\EH} framework.
+
+% \subsection{Entering a command}
+
+We assume that the user uses \tt{bash} for his software
+development activities.
+% 
+When a user wants to compare the latest \stt{README.md} file
+with the same file from 2 versions before,
+he might try to use {\GIT} with an option
+``{\smallfont\verb|HEAD^^|}''
+for specifying the old version.
+
+\begin{figure}[h]
+  {\smallfont
+  \verb|$ git diff HEAD^^ README.md|
+  \par
+  \verb|$|
+  }
+  \caption{Invoking \stt{git diff}.}
+  \label{gitdiff}
+\end{figure}
+
+% \begin{quotation}
+%   {\smallfont
+%   \verb|$ git diff HEAD^^ README.md|
+%   \par
+%   \verb|$|
+%   }
+% \end{quotation}
+
+However, nothing happens here because
+\verb|HEAD^^|
+specifies a file included in the older commit,
+and the command in figure \ref{gitdiff} only compares the
+\stt{README.md} with the file included in an old commit, where
+\stt{README.md} might not have changed since then.
+
+If {\GH} is installed,
+the user can type a special shortcut key
+% (e.g. \tt{Cmd-Ctrl-G})
+to invoke {\GH} after typing \sqtt{git RE 2} to see how he can
+perform the task.
+
+\begin{figure}[h]
+  % \includegraphics[width=9cm,bb=0 0 1194 822]{figures/example1.png}
+  \includegraphics[width=9cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
+  %\includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
+  \caption{Invoking {\GH} after typing \stt{git read 2}.}
+  \label{example1}
+\end{figure}
+
+Here, various candidate entries with
+descriptions and command strings are listed,
+just like text input support systems for non-English languages.
+One of the entries says
+``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}'',
+and if the user thinks that's what he wants to do,
+he can select the entry by typing arrow keys and type the enter key.
+Then the user's input string is replaced by the right command string
+that satisfies the user's need.
+
+A description like \sqsf{2 days ago} is also shown in the candidate list
+of Figure \ref{example1}.
+This means that the user can use the same string \sqtt{git RE 2}
+for getting the information of \stt{README.md} file of the day before yesterday.
+The generated argument
+``{\smallfont\verb|@{2 days ago}|}'',
+may not be familiar to most {\GIT} users,
+but users can perform this task only by giving \sqtt{RE} and \sqtt{2}
+without knowing the correct syntax of this option.
+
+When the user types a special shortcut key
+after typing \sqtt{git sh reed 3},
+entries related to \stt{README.md} file are listed because
+\sqtt{reed} is close to \sqtt{README.md}.
+
+\begin{figure}[h]
+  %\includegraphics[width=9cm,bb=0 0 1100 760]{figures/example2.png}
+  \includegraphics[width=9cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
+  \caption{Invoking {\GH} after typing \stt{git sh reed 3}.}
+  \label{example2}
+\end{figure}
+
+A Japanese {\GIT} user can do the same thing just like
+1vEnglish-speaking users (Figure \ref{example3}).
+He can use the term \qtt{表}, etc. to find how he can perform the job.
+
+\begin{figure}[t]
+  % bb=0 0 1290 866
+  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
+  \includegraphics[width=12cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
+  \caption{Invoking {\GH} in Japanese environment.}
+  \label{example3}
+\end{figure}
+
+If the user wants to know more about the command line,
+he can click the
+\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{../../GitHelp/paper/figures/info-xxl.png}}
+button and see the Wiki page shown in Figure \ref{scrapboxpage}.
+The user can edit the page if he wants to add information or finds an error.
+In this page, description part is preceded by a ``\texttt{\$}'' symbol and
+the command part is preceded by ``\texttt{\%}''.
+
+\begin{figure}[t]
+% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
+  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{../../GitHelp/paper/figures/scrapbox3.png}}
+  \caption{A {\SB} page for \tt{git diff}.}
+  \label{scrapboxpage}
+\end{figure}
+
 \subsection{OmniHelp}

### 2020-10-08 IUI2021/paper.tex
Implementation追加

@@
-%%
+%
+%
+%
 
@@
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
+\acmConference[IUI '21]{IUI '21: ACM Conference}
+  {June 03--05, 2020}{Somewhere, Italy}
 \acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
@@
 
+\subsection{ExpandHelp}
+
+A flexible help data retrieval mechanism ``{\EH}'' is used in {\GH}.
+%
+Help data used in {\EH} are provided as a set of data entries
+consisting of a regular expression that represents description of the help entry
+and a corresponding command pattern string.
+A description string is used to produce natural language texts
+that are easily understandable by users,
+while command patterns represents the generated command string
+corresponding to the description.
+%
+For example, a help entry for showing the difference between
+current file and older file can be defined like this:
+
+\begin{quote}
+  \textbf{description}: \\
+  \stt{Compare (\#\{files\}) with the one from (1|2|3|4) versions before}\\
+  \textbf{command}: \\
+  {\smallfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^|} \\
+  {\smallfont\verb| -- #{$1}|}
+\end{quote}
+
+Special symbols like \stt{\#\{files\}} in the description part is expanded to
+the list of filenames like \stt{README.md|index.html}.
+The first regular expression, the description part,
+is for generating texts like
+\sqsf{Compare README.md with the one from 1 versions before}, 
+\sqsf{Compare index.html with the one from 2 versions before}, etc.,
+and the second part, command part,
+is used to generate a command to execute a {\GIT} command.
+In the first example, \sqsf{README.md} and \sqsf{1}
+match the first and second parentheses of the regular expression, and
+these values are assigned to \tt{\$1} and \tt{\$2}
+for the command part, generating a command
+``{\smallfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^|}
+{\smallfont\verb|-- #{$1}|}''.
+
+The description part can be written in any natural language.
+For example,
+
+\begin{quote}
+  \stt{(\#\{files\})を(1|2|3|4)個前のものと比較する}
+\end{quote}
+
+can be used for Japanese users.
+In this case,
+\sqsf{README.mdを1個前のものと比較する},
+\sqsf{README.mdを2個前のものと比較する}, etc.
+are used for the matching.
+
+%% \subsection{(section written for GitHelp)}
+%% 
+%% {\EH} is a general-purpose flexible help generation system
+%% that has the following characteristics.
+%% 
+%% \begin{itemize}
+%% \item Use description-execution pairs for the translation
+%% \item Standard regular expression is used for the specification of the description
+%% \item The specification RegExp is expanded and filtered by the user's input string
+%%   real-time
+%% \end{itemize}
+%% 
+%% An example of the desc-exec pair can be the following:
+%% 
+%% \begin{verbatim}
+%%   (delete|remove) a (#{file})
+%%   /bin/rm $2
+%% \end{verbatim}
+%% 
+%% ``remove \verb|README.md|''
+%% into
+%% ``\verb|rm README.md|
+%% 
+%% First, the spec like \stt{\#\{file\}} is expanded to a list of filenames like
+%% \verb+README.md|Makefile|test.c+,
+%% and the spec string becomes
+%% ``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
+%% Then this regular expression is expanded to all the possible string that match this regexp like
+%% \begin{verbatim}
+%% delete a file README.md
+%% remove a file README.md
+%% delete a file Makefile
+%% remove a file Makefile
+%% ...
+%% \end{verbatim}
+%% 
+%% And then all these strings are compared with the user's specification like
+%% ``\verb|del REA|'',
+%% and if a match is found,
+%% this is translated to
+%% ``\verb|delete file README.md|''.
+%% 
+%% If ``\verb|destroy|'' should also be used for the spec,
+%% the spec can be modified to 
+%% \stt{(delete|remove) a (\#{file})}.
+%% 
+%% Any kind of specs in any language can be used for the specification.
+%% For example,
+%% 
+%% \begin{verbatim}
+%%   \#{file}を(消す|消去する)
+%%   /bin/rm $1
+%% \end{verbatim}
+%% 
+%% can be  used for Japanese users, who might want to delete
+%% one of the files by specifying ``消す''.
+%% (消す means 'delete' in Japanese).
+
+\subsubsection{Generating help menu entries}
+
+Finding appropriate entries from the (possibly huge) help document space is
+performed in two steps.
+First, a state transition diagram is generated from the regular expressions
+used in the descriptions.
+Second, all the description strings are generated by expanding the regular expression
+into a tree, and filter the generated strings by the pattern specified by the user.
+Efficient pattern matching is performed every time a new description text is generated,
+and only the best-matched descriptions are shown to the user as menu entries.
+We call this the ``\textit{generate-and-filter}'' technique,
+and we will describe the details later.
+
+\paragraph{Phase 1: Generating a state transition diagram from a regular expression}
+
+Regular expressions are widely used for finding patterns in text strings
+in modern programming languages and in the Unix environment.
+In {\EH}, we use regular expressions for
+generating various patterns of descriptions from a short specification.
+For example, we use a short regular expression
+\sqtt{(remove|delete|erase) (data|file)}
+for representing expressions like
+\sqsf{remove data},\sqsf{erase file}, etc.
+
+Converting a regular expression to a state transition machine is a
+straightforward task.
+When we have a regular expression
+\sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
+we can convert it into a state transition diagram
+shown in Figure \ref{statemachine1}.
+
+\begin{figure}[htb]
+\includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
+\caption{State transition diagram for a \stt{git} command description.}
+\label{statemachine1}
+\end{figure}
+
+By traversing the nodes and links in this state machine,
+we can generate the following description texts.
+
+\begin{quote}
+\small
+\ssf{Compare README.md with the one 1 versions before} \\
+\ssf{Compare index.html with the one 1 versions before} \\
+...\\
+\ssf{Compare package.json with the one 10 versions before}\\
+\end{quote}
+
+\paragraph{Phase 2: Generating texts from a state transition diagram}
+
+Using the state transition diagram shown in Figure \ref{statemachine1},
+{\EH} generates all the strings represented in the regular expressions,
+and filter them by the pattern provided by the user.
+
+We can generate texts from a state transition diagram by traversing nodes one by one.
+Starting at the start node
+(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
+in Figure \ref{statemachine1},
+we can visit other nodes via edges and generate a tree of generated texts
+shown in Figure \ref{gentree1}.
+After visiting the initial node
+\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
+the system generates a string \sqsf{Compare} and proceeds to the next node.
+In the second generation,
+the system can add \sqsf{README.md}, \sqsf{index.html}, and \sqsf{package.json}
+to \sqsf{Compare}, generating
+\sqsf{Compare README.md}, \sqsf{Compare index.html}, etc.
+The system can repeat finding edges from previously visited nodes,
+and eventually generates all the strings described above.
+Of course, it is impossible to generate all the strings
+from a regular expression like ``\tt{(0|1)+}'' that represents infinite length of
+strings consisting of \tt{0}s and \tt{1}s, so the generation should be
+terminated at a certain generation.
+
+\begin{figure}[htb]
+\includegraphics[width=85mm,bb=0 0 643 398]{figures/gentree1.pdf}
+\caption{Generating a text tree from a state transition machine.}
+\label{gentree1}
+\end{figure}
+
+\subsubsection{Generate-and-Filter}
+
+Generating all the texts in this way before finding matched strings is
+inefficient, because the amount of generated texts can easily become huge.
+Instead, the system performs the patter matching as soon as a text is generated,
+for saving time and memory.
+
+``Generate-and-test''\footnote{
+  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
+}
+is a simple and effective strategy used for solving puzzles.
+For example,
+the ``8-Queen'' problem can be solved simply by
+generating all the possible queen layouts and checking if
+two or more queens are laid out on the same row, column, or diagonal line.
+Although this strategy is simple, the cost of
+generating all the possible solutions is prohibitive, since
+the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
+which is not a small amount even for today's computers.
+
+To solve this problem,
+controlling the generation part from the testing part is effective.
+In the 8-Queen problem,
+whenever the testing part finds two queens in the same row or column,
+it can tell the generation part to
+give up current layout in the early stage and proceed to the next layout.
+
+Similarly in our case,
+it is not efficient to perform the matching operation
+after generating all the texts from the regular expression,
+and it is better to calculate the matching
+at the time of generating each text.
+We call it the \qit{generate-and-filter} strategy,
+and implemented the algorithm in {\EH}.
+Unlike simple puzzle problems where
+conditions are strict and finding one solution is enough,
+our goal is to find help description strings
+that fits the query pattern while allowing errors.
+For this goal,
+the system should perform approximate pattern matching
+without sacrificing processing speed.
+%
+We could implement flexible generate-and-filter by using a simple and efficient
+approximate pattern matching algorithm based on the ``shifter algorithm''.
+
+\subsubsection{Approximate pattern matching by shifter algorithm}
+
+The ``shifter algorithm''\cite{Wu:1992:FTS:135239.135244}
+is a simple and efficient
+text search algorithm that has interesting features
+not found in more common pattern matching algorithms like
+KMP\cite{KMP}, Boyer-Moor\cite{Boyer:1977:FSS:359842.359859}, etc.
+
+When a user wants to find a word \sqsf{README} in a text,
+he can use a patter matching state machine like below,
+where the gray circle denotes that the state is active.
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme1.pdf}}
+  \caption{A state machine for \qsf{README}.}
+  \label{readme1}
+\end{figure}
+
+Initially, only the leftmost node is active, but when the
+state machine receives \sqsf{R}, both the first and the second node become active,
+and the activation state will change to the following pattern.
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme2.pdf}}
+  \caption{After receiving \qsf{R}.}
+  \label{readme2}
+\end{figure}
+
+When \sqsf{README} is given to the state machine,
+the rightmost node becomes active.
+%
+%\begin{figure}[h]
+%\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme3.pdf}
+%\caption{After receiving \qsf{README}.}
+%\label{readme3}
+%\end{figure}
+
+Although this state machine is a nondeterministic finite state automata (NFA),
+only 7 bits are required to represent the active/inactive states of the nodes,
+meaning that the whole states can be represented by a single integer value.
+Also,
+the state transition can be calculated by a simple combination of
+logic and bit shift operations.
+
+\subsubsection{Approximate pattern matching using shifter algorithm}
+
+The state machine shown in Figure \ref{readme1} can accept only one pattern
+(\sqsf{README}), but
+it can be easily expanded to detect texts that contain a word
+similar to the pattern (e.g. \sqsf{REEDEE}).
+
+%   *  ** 
+%  risto rante
+%  restaurant
+% \begin{figure}[htb]
+%   \centerline{\includegraphics[width=30mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
+%   \caption{Matching error between \qsf{README} and \qsf{REEDEE}.}
+%   \label{readme-reddy-mismatch}
+% \end{figure}
+
+Adding three more rows of states to Figure \ref{readme1}, we can perform more
+flexible pattern matcher which can accept strings with
+0 to 3 matching errors.
+
+\begin{figure}[htb]
+  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-ambig.pdf}}
+  \caption{A pattern matcher accepting 0-3 errors.}
+  \label{shifterambig}
+\end{figure}
+
+Figure \ref{shifterambig} shows a state machine that can detect a string
+that matches \sqsf{README} with 0 to 3 mismatches.
+Each additional row of nodes represents a matcher with one error,
+two errors, and three errors, respectively.
+Vertical and diagonal transition edges are added to allow
+transitions based on spelling errors.
+
+Initially, only the bottom-left node is active.
+When a character other than \sqsf{R} is detected, 
+the transition labeled \sqsf{*} (wildcard) is activated,
+and connected nodes become active.
+At the same time, links labeled as ``$\epsilon$''
+is also activated without any input character.
+With these additional links, this expanded machine can detect a text which
+matches \sqsf{README} with 0 to 3 errors.
+
+\begin{figure}[htb]
+  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-reedee.pdf}}
+  \caption{Accepting \sqsf{REEDEE}'' using a matcher for \sqsf{README}.}
+  \label{readme-reedee}
+\end{figure}
+
+The transition of active nodes while reading
+\sqsf{REEDEE} is shown in Figure \ref{readme-reedee}.
+After reading \sqsf{REEDEE},
+only the upper-right node becomes active,
+denoting that \sqsf{REEDEE} matches
+\sqsf{README}'' with 2 matching errors.
+
+The state transition shown in 
+Figure \ref{readme-reedee} looks complicated, but
+the matching state can be represented by only four integer variables, and
+the matching algorithm can be implemented efficiently.
+
+\subsubsection{Using the matcher for generate-and-filter}
+
+We can use this approximate pattern matcher while generating
+help texts by traversing the state transition machine.
+%
+Every time a new node is generated by traversing an edge,
+matching state is calculated and stored in the generated node.
+The status pattern is calculated from the status pattern
+stored in the preceding node and the string associated with the edge.
+
+\begin{figure}[htb]
+  \centerline{\includegraphics[width=50mm,bb=0 0 302 230]{figures/RE_2.pdf}}
+  \caption{A pattern matcher for \sqtt{REE 2}.}
+  \label{RE_2}
+\end{figure}
+
+\begin{figure*}[bth]
+\centerline{\includegraphics[width=110mm,bb=0 0 643 446]{figures/gentree2.pdf}}
+\caption{Matching statuses for \sqtt{REE 2} associated with text generation nodes.}
+\label{gentree2}
+\end{figure*}
+
+Figure \ref{RE_2} shows the matcher for \sqtt{REE 2}\footnote{
+  A space (\qtt{ }) in the input is treated as a wildcard character.
+},
+and Figure \ref{gentree2} shows how the matching status is calculated while the
+description strings are generated from the state transition machine
+shown in Figure \ref{statemachine1}.
+The matching status at each node is calculated from the matching status
+stored in the parent node and the string associated with the edge.
+For example, when the system generates the string
+\qsf{Compare README.md with the one from 2 versions before},
+the matching status is calculated from the status data at the previous node at
+\qsf{Compare README.md with the one from 2}, and
+the system can tell that it matches \qtt{REE 2} with one matching error,
+as soon as the string is generated.
+
+The system is keeping the list of generated strings
+which match the pattern with zero to three errors
+and it displays the list with minimal number of errors
+when generating menu entries.
+% 
+Since the pattern matching operation is performed at the time of text generation,
+the whole generate-and-filter calculation is quick.
+
+% Although current version of ExpandHelp is implemented in MacRuby,
+% the user can always get the result within 1 second.
+% A portion of the help data in Ruby is shown in Figure \ref{helpdata}.
+
+% \begin{figure*}[bt]
+% \centerline{\includegraphics[width=146mm]{figures/04ad7dee5679450e5390821745b5a0b7.png}}
+% \caption{A portion of the help data in Ruby.}
+% \label{helpdata}
+% \end{figure*}
+
+\subsection{Sharing the database on the Web}
+
+The data used in {\GH} are represented as ``{\SB}'' documents
+shown in Figure \ref{scrapboxpage}.
+%
+{\SB} is a general-purpose real-time Wiki system for data sharing.
+{\SB} users can edit the contents of Wiki pages directly
+on Web browsers just like using text editors.
+
+% \begin{figure}[htb]
+% \begin{verbatim}
+% \end{verbatim}
+% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
+% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
+% \caption{A {\SB} page for \tt{git diff}.}
+% \label{xxxxx}
+% \end{figure}
+
+This page shows how to use \sqtt{git diff}, and
+the page contains command specifications in {\EH} format
+in addition to the documentation.
+
+% Specs and command lines are specified with a special symbol, and
+% all other documents can be written just like standard manuals and help documents.
+
+Usage examples are often shown on documents and manuals like Unix man pages,
+but they cannot be used as the database of an online help system.
+On the other hand,
+a {\SB} document contains both the manual document and the help database
+in the same place, just like
+writing a source code and the document in the same place
+under the ``Literate Programming''\footnote{
+  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Literate\_programming}
+} style.
+
+Also, since the database is on the Wiki page, any member of the
+Wiki can correct the document or add additional {\GH} specifications.
+When a user could not get a good support from {\GH}, he can add
+{\EH} specifications to the {\SB} document himself
+so that he and other people can get better support
+from {\GH} next time.
+
+\section{Related Work}
+
+\subsection{Intelligent help systems}
+
+There have long been many researches on
+intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
+but few number of projects seem to be going on these days,
+maybe because now we can use the Internet for getting intelligent help from
+real people,
+either by searching existing Web pages or 
+by asking in user forums like StackOverflow\footnote{
+  \textsf{https://stackoverflow.com/}
+}.
+Information on the net is rich these days, and we can easily
+find somebody who can give good answers to our questions.
+This is a good news, but 
+asking many trivial questions on the net is not considered to be a
+good manner, and
+using a powerful and flexible local help system like {\EH} is
+preferable most of the time.
+
+\subsection{Input Methods}
+
+Text input systems for non-English languages are widely used
+in the world,
+and they are called as ``Input Methods'' (IMs).
+%
+Many research and development on IMs have been going on for years, and
+people are using them every day for entering texts in their mother language.
+Figure \ref{gyaim} shows an example of a Japanese IM.
+
+\begin{figure}[H]
+  % \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
+  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}}
+  \caption{An IM for Japanese text input.}
+  \label{gyaim}
+\end{figure}
+
+IMs are one form of translation systems that convert one
+expression (pronunciation, character shape, etc.)
+into a textual form of a language.
+In the above example, the pronunciation ``kanji''
+is used for getting ``漢字''.
+
+IMs are very popular in the modern computing environment in the world
+and it is very common for people to 
+use translation systems for using computers.
+%
+The behavior of {\GH} is similar to conventional IMs, and
+integration of multiple IM-like systems should be challenged in the future.
+
+\subsection{Text and code completion}
+
+On text editors and Unix shells,
+``text completion'' feature has been available for a long time.
+%
+When a user types the TAB key after typing \sqtt{la} on the Unix shell,
+\sqtt{latex}, \sqtt{last}, and other Unix commands are shown as candidates.
+When a user types \sqtt{ls RE} and types the TAB key,
+the shell checks the directory, find the \stt{README.md} file, and
+replace the user's input with \sqtt{ls README.md}.
+This behavior is called ``text completion'', and many variations of
+this idea have been proposed and adopted in command shells and text editors.
+
+% User's history data can also be used for the completion function.
+% The Reactive Keyboard\cite{ReactiveKeyboard}
+% accumulates the user's command history and use the data
+% for predicting the user's next input.
+
+Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
+helps {\GIT} users by
+dynamically showing possible arguments and related manuals on the Unix shell,
+just like {\GH} does.
+The goal of Gitsome is almost the same as {\GH} and we agree with its concept,
+but Gitsome does not support flexible approximate matching and
+help data sharing.
+
+\subsection{Smart IDEs}
+
+Integrated Development Environments (IDEs) are widely used for
+software development, and
+many smart IDEs for suggesting codes have been proposed recently.
+
+Little's system\cite{Little:2006:TKC:1166253.1166275}
+generates a complete JavaScript code snippet from keyword fragments
+give by users.
+For example, a code snippet
+\sqtt{ActiveDocument.PageSetup.LeftMargin = InchesToPoints(2)}
+can be generated from keywords like
+\sqsf{left},
+\sqsf{margin},
+\sqsf{inches},
+and \sqsf{2}.
+The system generates the code using a template database and heuristics
+designed for the target system.
+It is useful for a specific environment, but
+users of the system cannot modify the algorithm or the database
+even when no good suggestion was found.
+
+% キーワードの羅列からコマンドを作成するという考えはとても正しいと思うが、実装がいかがなものか?
+% キーワードぐらいは思い出せるプログラマが対象になっている
+% 「margin」とか「left」とかいう単語は思い出す必要がある
+% 「ちょっと字下げ」とか言っても駄目
+% キーワードが違ってると駄目?
+% いろいろズルをしてるようだ
+% [[ActiveDocument]]はよく出てくるので特別扱いしているとか
+% ステミングをしている
+% ``the'' ``to'' などは捨ててるのだろう
+% そもそもリカーシブな検索アルゴリズムにかなり無理がありそう
+% テンプレートを作るのは大変ではないのか?
+
+% https://www.youtube.com/watch?v=93vZAmLyOQY
+AnyCode\cite{Gvero:2015:SJE:2814270.2814295} is another system
+that generates a complete code snippet from the user's
+input in natural language.
+AnyCode can handle synonyms database like ``make'' == ``create'',
+but approximate matching is not supported and
+users cannot modify the help database.
+
+% 曖昧検索はできず、かなりキーワードを指定する必要はある
+
+% [anyCode]というシステム。自然言語キーワードを入力するとコードスニペットが表示される。
+% [[copy fileA fileB]]みたいなキーワードから[[FileUtil.copyFile(new File(fileA), new File(fileB))]]みたいなコード候補を生成する
+% [自然言語処理]を行なっている
+% [https://github.com/tihomirg/nlpcoder/tree/noola GitHub]
+% 曖昧検索はできない
+% 真面目に自然言語を入れる必要がある
+% `123`みたいなパラメタは使えるか?
+% 使えると思うが例には出てこない
+% コードの説明文は出ない?
+% FileUtil.copyFile(new File(fileA), new File(fileB)) と言われても、どちらが新しいファイルなのかわからない
+
+Active Code Completion\cite{Omar:2012:ACC:2337223.2337324}
+is another code completion system for the Eclipse IDE.
+A database called \textit{palette} are used for code completion and coding support
+for Java classes.
+When a user wants to write a code for drawing a rectangle in purple,
+the user should just tell ``purple'' to the system,
+and the system shows the user a color selection window
+as well as the Java code for drawing a purple rectangle.
+This is a useful feature for the user to write a code including selecting
+a color, but palettes are difficult to create, and should be provided
+as IDE plugins.
+% [/ palette] と呼ばれるテンプレートを用意して[IDE]でのコード補完をサポートする
+% `getDefaultColor()` を定義したいとき`purple`と入力すると、それに対応した候補が提示されるとか
+% 普段使ってる環境で有益な候補が表示されると嬉しいだろうと言っている
+% [[コメント]]
+% [Jun Kato.icon]
+% > Active code completionも思い出しました。型ごとに適した入力インタフェースを出すコード補完インタフェースのnn提案です。確か。
+% [増井俊之.icon]
+% IDEでどういう機能が欲しいかサーベイして設計したことになっている
+% 色選択と正規表現のためのコード生成をサポートした例が紹介されている
+% 一般的な補完コマンド起動によって呼び出されるようだ
+% サポートウィンドウはHTML5で生成する
+% しかし両者とも[/palette]の作成はかなり大変である
+% 普通のユーザが作れるようなものではない
+% [* 作成がすごく大変]で、[* 特定のIDEでしか使えない]という問題があると思う
+
+Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
+can generate a code snippet from abbreviation strings give by the user.
+For example, a code snippet like \sqtt{chooser. showOpenDialog()}
+can be generated from strings like
+\sqsf{ch} and \sqsf{opn}, using the code database and HMM.
+It can be very useful as a shorthand for handling long names,
+but users should have a vague knowledge about the correct names
+(e.g. \sqtt{chooser}, \sqtt{dialog}),
+and large code example corpus should exist before being able to
+create the database.
+{\EH} database can be created by hand at the time of the system development
+and no corpus is required.
+
+% [HMM]を使って正しいコードを予測して提示する
+% `ch opn`みたいなテキトーな入力から`chooser.showOpenDialog()`みたいな正しいコードが候補に出る
+% コードデータベースを解析
+% [[コメント]]
+% [増井俊之.icon] 2018/3/23 18:53
+% コードのほんの一部を指定すると正しく予測されるというのは面白い
+% HMMってそういうのに使えるのね
+% しかし[* 関数名とか全然覚えていないときは使えないだろう]
+% [語彙問題]が解決できてない
+% だとすると高速入力の役にはたつが、何もかもわからない人をサポートはできない
+% 用例データが存在しない場合も使えない
+% [IDE]でしか使えない
+% [Cyrus Omar: Active code completion]で参照されている
+
+\subsection{Using cloud data for development}
+
+% 他人の情報利用する系
+% コード共有、コンパイルエラー共有
+
+Many systems support sharing users' development experiences on the web so that
+they can be used on the developers' IDE.
+
+Using BluePrint\cite{Brandt:2010:EPI:1753326.1753402}
+as a plugin for Adobe Flex Builder,
+users can search sample codes from the Web and use it immediately.
+%   サンプルコードをすぐ参照して利用できる[IDE]
+%
+HelpMeOut\cite{Hartmann:2010:OPS:1753326.1753478} tells users
+how to handle compile errors,
+based on the people's experiences of handling compile errors.
+%
+Resources on the net are precious, and such data can be
+easily incorporated to {\EH} databases.
+
+%= 他人のヒストリを使ってコンパイルエラー対処法をサジェスト
+
+% \subsection{Literate Programming}
+% 
+% Literate Programming\cite{Knuth}
+% 
+% 参考文献にすることはないか
+% 
+% JavaDoc
+% Jupyter
+% Eve
+
 \section{Discussions}
@@
 
+\paragraph{Applications of ExpandHelp}
+
+Since the translation mechanism of {\EH} is simple and flexible,
+it can be used for a wide range of application domains where
+intelligent help is required.
+{\EH} is actually used as the help page for
+one of our Web services, hoping that
+novice users can easily find the feature they need.
+When a user submits a query that includes vocabularies
+not in the {\EH} document,
+we are able to add them to the {\SB} database easily.
+
+Figure \ref{mac1} and Figure \ref{mac2} shows how
+{\EH} can be used as a launcher for MacOS.
+Like {\GH}, users can execute concrete commands only by
+showing small fragments of their intentions to the system.
+
+\begin{figure}[h]
+  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{figures/clock.png}}
+  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{figures/mac1.png}}
+  \caption{Using {\EH} in the menu bar of MacOS.}
+  \label{mac1}
+\end{figure}
+
+\begin{figure}[h]
+  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{figures/mac2.png}}
+  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{figures/mac2.png}}
+  \caption{Using {\EH} in the menu bar of MacOS.}
+  \label{mac2}
+\end{figure}
+
+\paragraph{Order of command and arguments}
+
+Using a command shell,
+users have to enter a command first and enter options and arguments after that.
+Using a GUI desktop,
+users can right-click a data icon to show a menu,
+and select what he wants to do from the menu.
+Switching between command-oriented usage pattern and
+data-oriented usage pattern is sometimes confusing.
+Using {\EH}, users can find what they can do
+either by specifying commands or by specifying data, 
+without worrying about the order.
+
+\paragraph{Usage of regular expressions}
+
+An advantage of using a regular expression is that
+it is fairly easy for users to write description texts.
+People can easily write a help description like
+\sqtt{(Start|Run) Firefox browser}
+without having a knowledge of automata or formal grammar.
+We can use arbitrary texts for the database of {\EH}.
+For example,
+we can collect hundreds of books titled ``Windows tips'' from the market
+and convert all the title of the tips into help data of {\EH}.
+
+\section{Conclusion}
+
+We proposed the ``translation paradigm'' for bridging the gap between
+users' intention and actual operations.
+%
+We have introduced a general-purpose flexible framework {\EH}
+that can translate fragments of user's vague intentions into
+concrete command strings required to control computers and
+other complex artifacts.
+We showed the principles and applications of {\EH} by using it
+for {\GH}, a help system for supporting {\GIT} users
+based on the shared database that any user can edit to share
+translation knowledge between users.
+%
+{\EH} framework is useful for any kind of systems that need
+some kind of user support, and we are planning to use it
+for various applications and Web services in the future.
+
+% Unlike existing smart IDEs for supporting programming tasks,
+% {\EH} framework can be used in wide range of situations
+% where translation-based help is required.
+% 
+% Using the powerful and flexible help system ``{\EH}''
+% constructed on the generate-and-filter algorithm, where
+% the system generates all the possible expressions of
+% help entries expanded from regular expressions,
+% while the output expressions are filtered by search keywords using
+% an efficient approximate pattern matching algorithm.
+% 
+% Since the data format is simple and the search algorithm is fast and flexible,
+% developers can easily publish useful help data, while
+% users can have bigger chances of finding an appropriate
+% data from vague knowledges.
+
+% References must be the same font size as other body text.
+
+%\bibliographystyle{SIGCHI-Reference-Format}
+%\bibliography{paper}
+
 \end{document}

### 2020-10-09 IUI2021/paper.tex
generate.rbは実験中...

@@
 
-\def\GH{\textsf{GitHelp}}
+\def\HL{\textsf{HelpLine}}
+\def\HF{\textsf{Helpfeel}}
 \def\GIT{\texttt{git}}
-\def\EH{\textsf{ExpandHelp}}
+\def\ES{\textsf{ExpandSearch}}
 \def\SB{\textsf{Scrapbox}}
@@
   the user's search keyword does not exist in the document.
-  Providing entries for ExpandSearch can solve the problem, but
+  Providing entries for {\ES} can solve the problem, but
 
@@
 
-\subsection{Helpfeel}
-
-We have been applying ExpahdSearch for various customer support services on existing Web services.
-The help system based on ExpandSearch is called \textit{Helpfeel}, and
-
-Helpfeel is a FAQ engine that supports users who do not have enough vocabulary for the Web services they want to use.
-
-% ここでどこかのサポートシステムを示す
-
-Figure xxx shows an example Helpfeel page that supports finding FAQs
-for PayPay Free market run by Yahoo! Japan.
-We provide the description on the Scrapbox wiki service,
-
-% https://paypayfleamarket.yahoo.co.jp/help/
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
-  \caption{PayPay Freemarket}
-  \Description{PayPay}
-\end{figure}
+% [[ExpandSearchの実例]]
+%  まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
+% [[実例1]] ExpandHelpの実際の利用
+%  ScrapboxというWiki上にいろんな表現を用意しておく
+%  Helpfeel
+%   PayPayフリマなどですごく効率があがった
+%  実際これによりヘルプ問い合わせは劇的に減る (出典: Helpfeel)
+% [[実例2]] 検索インタフェースの融合
+%  マイHelpfeel
+%  検索をひとつの方法に統合する
+%   検索方法が複数だと面倒臭い
+%    ググって出なければ逆引き辞典を検索する、みたいなのは面倒
+%   同じ検索インタフェースでいろんなところを探すほうが簡単である
+%   どこにメモしたか忘れて困ることがなくなる
+%  自分のデータが増えていく状況のグラフを書ける!
+% 
+% [[実例3]]
+%  gitのヘルプ - コマンドラインで動くもの
+%   パラメタを指定して実行につなげることすらできる
 
@@
 
-We created the GitHelp system using ExpandHelp, so that git users can easily
+We created the GitHelp system using {\ES}, so that git users can easily
 remember command options and use it without perfectly remembering the git commands.
 
-----------------------------
-
-We implemented the {\GH} system
+We implemented the HelpLine system
 with which a user can translate his vague intention in various languages
 into a complete {\GIT} command
-using the {\EH} framework.
+using the {\ES} framework.
 
@@
 \begin{figure}[h]
-  {\smallfont
-  \verb|$ git diff HEAD^^ README.md|
-  \par
-  \verb|$|
+  \vbox{
+    \begin{verbatim}
+      $ git diff HEAD^^ README.md
+      $
+    \end{verbatim}
   }
@@
 \end{figure}
-
-% \begin{quotation}
-%   {\smallfont
-%   \verb|$ git diff HEAD^^ README.md|
-%   \par
-%   \verb|$|
-%   }
-% \end{quotation}
 
@@
 
-If {\GH} is installed,
+If HelpLine is installed,
 the user can type a special shortcut key
-% (e.g. \tt{Cmd-Ctrl-G})
-to invoke {\GH} after typing \sqtt{git RE 2} to see how he can
+(e.g. \texttt{Ctrl-J})
+to invoke HelpLine after typing \sqtt{git RE 2} to see how he can
 perform the task.
@@
 \begin{figure}[h]
-  % \includegraphics[width=9cm,bb=0 0 1194 822]{figures/example1.png}
   \includegraphics[width=9cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
-  %\includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
-  \caption{Invoking {\GH} after typing \stt{git read 2}.}
+  \caption{Invoking {\HL} after typing \stt{git read 2}.}
   \label{example1}
@@
 
-Here, various candidate entries with
-descriptions and command strings are listed,
+Here, various candidate entries with descriptions and command strings are listed,
 just like text input support systems for non-English languages.
@@
 and if the user thinks that's what he wants to do,
-he can select the entry by typing arrow keys and type the enter key.
+he can select the entry by typing arrow keys and the enter key.
 Then the user's input string is replaced by the right command string
@@
 
-When the user types a special shortcut key
+When the user types the shortcut key
 after typing \sqtt{git sh reed 3},
+approximate pattern matching is automatically performed, and
 entries related to \stt{README.md} file are listed because
-\sqtt{reed} is close to \sqtt{README.md}.
+\sqtt{reed} matches \sqtt{README.md} with one error.
 
 \begin{figure}[h]
-  %\includegraphics[width=9cm,bb=0 0 1100 760]{figures/example2.png}
   \includegraphics[width=9cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
-  \caption{Invoking {\GH} after typing \stt{git sh reed 3}.}
+  \caption{Invoking {\HL} after typing \stt{git sh reed 3}.}
   \label{example2}
@@
 A Japanese {\GIT} user can do the same thing just like
-1vEnglish-speaking users (Figure \ref{example3}).
+English-speaking users (Figure \ref{example3}).
 He can use the term \qtt{表}, etc. to find how he can perform the job.
@@
 \begin{figure}[t]
-  % bb=0 0 1290 866
-  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
   \includegraphics[width=12cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
-  \caption{Invoking {\GH} in Japanese environment.}
+  \caption{Invoking {\HL} in Japanese environment.}
   \label{example3}
@@
 \begin{figure}[t]
-% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
   \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{../../GitHelp/paper/figures/scrapbox3.png}}
@@
 
-\subsection{OmniHelp}
-
-OmniHelp is an implementation of ExpandHelp that runs on Chrome browser.
+\subsection{OmniSearch}
+
+OmniSearch is an implementation of ExpandSearch that runs on Chrome browser.
 The URL window on Chrome is called omnibox,
 
-\begin{verbatim}
-[[ExpandSearchの実例]]
- まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
-[[実例1]] ExpandHelpの実際の利用
- ScrapboxというWiki上にいろんな表現を用意しておく
- Helpfeel
-  PayPayフリマなどですごく効率があがった
- 実際これによりヘルプ問い合わせは劇的に減る (出典: Helpfeel)
-[[実例2]] 検索インタフェースの融合
- マイHelpfeel
- 検索をひとつの方法に統合する
-  検索方法が複数だと面倒臭い
-   ググって出なければ逆引き辞典を検索する、みたいなのは面倒
-  同じ検索インタフェースでいろんなところを探すほうが簡単である
-  どこにメモしたか忘れて困ることがなくなる
- 自分のデータが増えていく状況のグラフを書ける!
-
-[[実例3]]
- gitのヘルプ - コマンドラインで動くもの
-  パラメタを指定して実行につなげることすらできる
-\end{verbatim}
+\subsection{Helpfeel}
+
+We have been applying ExpahdSearch for various customer support services on existing Web services.
+The help system based on {\ES} is called {\HF}, and
+
+{\HF} is a FAQ engine that supports users who do not have enough vocabulary for the Web services they want to use.
+
+% ここでどこかのサポートシステムを示す
+
+Figure xxx shows an example {\HF} page that supports finding FAQs
+for PayPay Free market run by Yahoo! Japan.
+We provide the description on the Scrapbox wiki service,
+
+% https://paypayfleamarket.yahoo.co.jp/help/
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
+  \caption{PayPay Freemarket}
+  \Description{PayPay}
+\end{figure}
 
@@
 
-\subsection{ExpandHelp}
-
-A flexible help data retrieval mechanism ``{\EH}'' is used in {\GH}.
-%
-Help data used in {\EH} are provided as a set of data entries
-consisting of a regular expression that represents description of the help entry
+\subsection{ExpandSearch}
+
+A flexible search mechanism ``ExpandSearch'' is used in HelpLine.
+%
+The database used in ExpandSearch are provided as a set of data entries
+consisting of a regular expression that represents description of the data entry
 and a corresponding command pattern string.
@@
   \textbf{command}: \\
-  {\smallfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^|} \\
-  {\smallfont\verb| -- #{$1}|}
+  {\smallfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}
 \end{quote}
@@
 
-can be used for Japanese users.
+can be used for Japanese {\GIT} users.
 In this case,
@@
 in modern programming languages and in the Unix environment.
-In {\EH}, we use regular expressions for
+In {\ES}, we use regular expressions for
 generating various patterns of descriptions from a short specification.
@@
 When we have a regular expression
-\sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
+\sqtt{Compare (README.md|index.html|package.json) with the one from (1|2|...|10) versions before}, 
 we can convert it into a state transition diagram
@@
 \begin{figure}[htb]
-\includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
+\includegraphics[width=90mm,bb=0 0 571 126]{../../GitHelp/paper/figures/statemachine.pdf}
 \caption{State transition diagram for a \stt{git} command description.}
@@
 Using the state transition diagram shown in Figure \ref{statemachine1},
-{\EH} generates all the strings represented in the regular expressions,
+{\ES} generates all the strings represented in the regular expressions,
 and filter them by the pattern provided by the user.
@@
 Starting at the start node
-(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
+(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{../../GitHelp/paper/figures/startnode.pdf}})
 in Figure \ref{statemachine1},
@@
 After visiting the initial node
-\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
+\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{../../GitHelp/paper/figures/startnode.pdf}},
 the system generates a string \sqsf{Compare} and proceeds to the next node.
@@
 \begin{figure}[htb]
-\includegraphics[width=85mm,bb=0 0 643 398]{figures/gentree1.pdf}
+\includegraphics[width=85mm,bb=0 0 643 398]{../../GitHelp/paper/figures/gentree1.pdf}
 \caption{Generating a text tree from a state transition machine.}
@@
 We call it the \qit{generate-and-filter} strategy,
-and implemented the algorithm in {\EH}.
+and implemented the algorithm in {\ES}.
 Unlike simple puzzle problems where
@@
 \begin{figure}[h]
-  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme1.pdf}}
+  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{../../GitHelp/paper/figures/readme1.pdf}}
   \caption{A state machine for \qsf{README}.}
@@
 \begin{figure}[h]
-  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme2.pdf}}
+  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{../../GitHelp/paper/figures/readme2.pdf}}
   \caption{After receiving \qsf{R}.}
@@
 
-%   *  ** 
-%  risto rante
-%  restaurant
 % \begin{figure}[htb]
@@
 \begin{figure}[htb]
-  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-ambig.pdf}}
+  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{../../GitHelp/paper/figures/readme-ambig.pdf}}
   \caption{A pattern matcher accepting 0-3 errors.}
@@
 \begin{figure}[htb]
-  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-reedee.pdf}}
+  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{../../GitHelp/paper/figures/readme-reedee.pdf}}
   \caption{Accepting \sqsf{REEDEE}'' using a matcher for \sqsf{README}.}
@@
 \begin{figure}[htb]
-  \centerline{\includegraphics[width=50mm,bb=0 0 302 230]{figures/RE_2.pdf}}
+  \centerline{\includegraphics[width=50mm,bb=0 0 302 230]{../../GitHelp/paper/figures/RE_2.pdf}}
   \caption{A pattern matcher for \sqtt{REE 2}.}
@@
 \begin{figure*}[bth]
-\centerline{\includegraphics[width=110mm,bb=0 0 643 446]{figures/gentree2.pdf}}
+\centerline{\includegraphics[width=110mm,bb=0 0 643 446]{../../GitHelp/paper/figures/gentree2.pdf}}
 \caption{Matching statuses for \sqtt{REE 2} associated with text generation nodes.}
@@
 % \begin{figure*}[bt]
-% \centerline{\includegraphics[width=146mm]{figures/04ad7dee5679450e5390821745b5a0b7.png}}
+% \centerline{\includegraphics[width=146mm]{../../GitHelp/paper/figures/04ad7dee5679450e5390821745b5a0b7.png}}
 % \caption{A portion of the help data in Ruby.}
@@
 
-The data used in {\GH} are represented as ``{\SB}'' documents
+The data used in {\HL} are represented as ``{\SB}'' documents
 shown in Figure \ref{scrapboxpage}.
@@
 % \end{verbatim}
-% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
-% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
+% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{../../GitHelp/paper/figures/scrapbox1.png}}
+% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{../../GitHelp/paper/figures/scrapbox1.png}}
 % \caption{A {\SB} page for \tt{git diff}.}
@@
 This page shows how to use \sqtt{git diff}, and
-the page contains command specifications in {\EH} format
+the page contains command specifications in {\ES} format
 in addition to the documentation.
@@
 Also, since the database is on the Wiki page, any member of the
-Wiki can correct the document or add additional {\GH} specifications.
-When a user could not get a good support from {\GH}, he can add
-{\EH} specifications to the {\SB} document himself
+Wiki can correct the document or add additional {\HL} specifications.
+When a user could not get a good support from {\HL}, he can add
+{\ES} specifications to the {\SB} document himself
 so that he and other people can get better support
-from {\GH} next time.
+from {\HL} next time.
 
@@
 good manner, and
-using a powerful and flexible local help system like {\EH} is
+using a powerful and flexible local help system like {\ES} is
 preferable most of the time.
@@
 \begin{figure}[H]
-  % \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
-  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}}
+  % \includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}
+  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}}
   \caption{An IM for Japanese text input.}
@@
 %
-The behavior of {\GH} is similar to conventional IMs, and
+The behavior of {\HL} is similar to conventional IMs, and
 integration of multiple IM-like systems should be challenged in the future.
@@
 dynamically showing possible arguments and related manuals on the Unix shell,
-just like {\GH} does.
-The goal of Gitsome is almost the same as {\GH} and we agree with its concept,
+just like {\HL} does.
+The goal of Gitsome is almost the same as {\HL} and we agree with its concept,
 but Gitsome does not support flexible approximate matching and
@@
 create the database.
-{\EH} database can be created by hand at the time of the system development
+{\ES} database can be created by hand at the time of the system development
 and no corpus is required.
@@
 Resources on the net are precious, and such data can be
-easily incorporated to {\EH} databases.
+easily incorporated to {\ES} databases.
 
@@
 
-Since the translation mechanism of {\EH} is simple and flexible,
+Since the translation mechanism of {\ES} is simple and flexible,
 it can be used for a wide range of application domains where
 intelligent help is required.
-{\EH} is actually used as the help page for
+{\ES} is actually used as the help page for
 one of our Web services, hoping that
@@
 When a user submits a query that includes vocabularies
-not in the {\EH} document,
+not in the {\ES} document,
 we are able to add them to the {\SB} database easily.
@@
 Figure \ref{mac1} and Figure \ref{mac2} shows how
-{\EH} can be used as a launcher for MacOS.
-Like {\GH}, users can execute concrete commands only by
+{\ES} can be used as a launcher for MacOS.
+Like {\HL}, users can execute concrete commands only by
 showing small fragments of their intentions to the system.
@@
 \begin{figure}[h]
-  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{figures/clock.png}}
-  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{figures/mac1.png}}
-  \caption{Using {\EH} in the menu bar of MacOS.}
+  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
+  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
+  \caption{Using {\ES} in the menu bar of MacOS.}
   \label{mac1}
@@
 \begin{figure}[h]
-  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{figures/mac2.png}}
-  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{figures/mac2.png}}
-  \caption{Using {\EH} in the menu bar of MacOS.}
+  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
+  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
+  \caption{Using {\ES} in the menu bar of MacOS.}
   \label{mac2}
@@
 data-oriented usage pattern is sometimes confusing.
-Using {\EH}, users can find what they can do
+Using {\ES}, users can find what they can do
 either by specifying commands or by specifying data, 
@@
 without having a knowledge of automata or formal grammar.
-We can use arbitrary texts for the database of {\EH}.
+We can use arbitrary texts for the database of {\ES}.
 For example,
 we can collect hundreds of books titled ``Windows tips'' from the market
-and convert all the title of the tips into help data of {\EH}.
+and convert all the title of the tips into help data of {\ES}.
 
@@
 %
-We have introduced a general-purpose flexible framework {\EH}
+We have introduced a general-purpose flexible framework {\ES}
 that can translate fragments of user's vague intentions into
@@
 other complex artifacts.
-We showed the principles and applications of {\EH} by using it
-for {\GH}, a help system for supporting {\GIT} users
+We showed the principles and applications of {\ES} by using it
+for {\HL}, a help system for supporting {\GIT} users
 based on the shared database that any user can edit to share
@@
 %
-{\EH} framework is useful for any kind of systems that need
+{\ES} framework is useful for any kind of systems that need
 some kind of user support, and we are planning to use it
@@
 % Unlike existing smart IDEs for supporting programming tasks,
-% {\EH} framework can be used in wide range of situations
+% {\ES} framework can be used in wide range of situations
 % where translation-based help is required.
 % 
-% Using the powerful and flexible help system ``{\EH}''
+% Using the powerful and flexible help system ``{\ES}''
 % constructed on the generate-and-filter algorithm, where

### 2020-10-09 lib/helpline/generate.rb

@@ -22,7 +22,7 @@ class HelpLine
     #
     # HelpLineエントリ
     #
-
+    # debug = true
     logfile = (debug ? "/tmp/helpline-defs" : "/dev/null")
     File.open(logfile,"w"){ |f|  # ログを残す場合
       entries = []
@@ -35,7 +35,7 @@ class HelpLine
             desc = eval('"' + l + '"')
             f.puts "desc: #{desc}"
             g.add desc.force_encoding('utf-8'), cmd.force_encoding('utf-8')
-            # puts "g.add(\"#{desc.force_encoding('utf-8')}\",\"#{cmd.force_encoding('utf-8')}\")"
+            # f.puts "g.add(\"#{desc.force_encoding('utf-8')}\",\"#{cmd.force_encoding('utf-8')}\")"
           }
           f.puts "cmd:  #{cmd}"
           entries = []
@@ -43,14 +43,24 @@ class HelpLine
       }
     }
 
+    # generateは曖昧検索も行なう => res[0], res[1], res[2] にそれぞれ入る
     res = g.generate query
 
     File.open("/tmp/helpline.cmd","w"){ |f|
+      f.puts "query = <#{query}>"
+      f.puts "--------------------"
       f.puts ARGV.join(' ')
+      f.puts "--------------------"
+      f.puts res[0]
+      f.puts "--------------------"
+      f.puts res[1]
+      f.puts "--------------------"
+      f.puts res[2]
     }
 
     listed = {}
-    list = res[0].find_all { |a| # 0 ambig
+    # list = res[0].find_all { |a| # 0 ambig
+    list = res[1].find_all { |a| # 1 ambig
       # a = ["git: 現在の状況を表示する {56}", "git status {56}"], etc.
       if a[0] =~ /voidvoidvoid/
         false

### 2020-10-09 IUI2021/paper.tex
...

@@
   We have been using this document expansion technique called
-  ExpandSearch for several years, and the system is working on various
+  {\ES} for several years, and the system is working on various
   commercial Web services. In this paper, we describe the idea and
-  implementation of ExpandHelp and show how it works in the wild.
+  implementation of {\ES} and show how it works in the wild.
 \end{abstract}
@@
 People are frequently searching information using keywords on Google
-and other systems, but keyword search is still not an easy task,
+and other systems.
+But keyword search is still not an easy task,
 because it is fundamentally difficulto to find appropriate information
@@
 
-The help system of MacOS (Catalina v10.15.5) does not tell a user how to remove a file.
+The help system of MacOS (Catalina v10.15.5) cannot tell us how to remove a file.
 
@@
   \centering
-  \includegraphics[width=10cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
-  \caption{Asking the help application how to remove a file.}
+  \includegraphics[width=12cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
+  \caption{Asking the help application on Mac how to remove a file.}
   \Description{Mac Mac}
@@
   \centering
-  \includegraphics[width=10cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
+  \includegraphics[width=12cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
   \caption{Mac}
@@
 
-We can get this kind of information fairly easily using search systems on Internet,
+We can get this kind of information fairly easily using search systems on the net,
 so many people prefer getting information using search engines rather than
@@
 If there are documens that contain ``remove'', ``file'', and ``Mac'',
-finding such documents are not easy.
-
-That seems to be the main reason why people are satisfied with search engines on the net
-for finding popular? information.
+finding such documents are not difficult.
+That seems to be the main reason why people are satisfied with search engines
+for finding popular information.
 
@@
 finding a less popular information is rather difficult,
-because not enough document related to the topic is found on the net.
-
+because not enough documents related to the topic is found on the net.
+%
 If there is only one document on the net
@@
 
-FAQs provided by service providers are not usually considered useful
+FAQs (frequently asked questions) provided by service providers are
+usually not considered useful
 because the terms used by the people on the service are usually
-different from the word that user can think of.
+different from the keywords that user can imagine.
 
@@
 Even finding the users' old documents can be sometimes difficult,
-because people might use different keywords for the same
-thing. He might try to find a file on "ZZZ" and fail, because he used
-the term "WWW" before.
+because people might use different keywords for the same thing case by case.
+He might try to find a file related to ``IUI'' and fail, because he used
+the term ``intelligent user interface'' for the file name.
+%
+Various techniques have been proposed to solve this vocabulary problem,
+but not very successful enough.
 
@@
 %  良いファイル名をつけたつもりでも後から検索できないことがある
-
-Various techniques have been proposed to solve this vocabulary problem.
-But not very successful.
 
@@
 manual of the system is written in French,
-he has to \textbf{translate} the term ``delete'' and ``file''
+he has to translate the term ``delete'' and ``file'' into French
 before the search.
@@
 translating the word in their brain into English words
-before searching on the net.
+before searching information, because important information are
+usually provided in English.
 
@@
 
+% Query expansion (QE) is the process of reformulating a given query to
+% improve retrieval performance in information retrieval operations,
+% particularly in the context of query understanding.[1] In the context
+% of search engines, query expansion involves evaluating a user's input
+% (what words were typed into the search query area, and sometimes other
+% types of data) and expanding the search query to match additional
+% documents. Query expansion involves techniques such as:
+% 
+% * Finding synonyms of words, and searching for the synonyms as well
+% * Finding semantically related words (e.g. antonyms, meronyms, hyponyms, hypernyms)
+% * Finding all the various morphological forms of words by stemming each word in the search query
+% * Fixing spelling errors and automatically searching for the corrected form or suggesting it in the results
+% * Re-weighting the terms in the original query
+%
+% Query expansion is a methodology studied in the field of computer
+% science, particularly within the realm of natural language processing
+% and information retrieval.
+
 The vocabulary problem and the translation problem can be solved
 if the search system have a thesaurus and a translation dictionary.
-
+%
 For example, 
@@
 even when the user specified the keyword ``remove''.
-
-This kind of technique is called \textit{Query expansion}, and simple query
+%
+This kind of technique is called ``\textit{Query expansion}'', and simple query
 expansion is possible if proper dictionary is provided.
@@
 Query expansion is effective when simple substitution of keywords are satisfactory enough.
-Using 'delete' in addition to 'remove' works...
+In the previous example, using the keyword ``delete'' in addition to ``remove'' works
+for finding the manual entry.
 
@@
 
-  The main idea for solving the problem is 
-  providing \textbf{regular expressions} (REs)
+  Our main idea for solving the problem is 
+  providing regular expressions (REs)
   for  each document so that a wide variety of user queries can match one of the
@@
   works quite effectively for almost all search activities.
-  Using the ExpandHelp algorithm, all the expressions are expanded in advance,
+  Using the ExpandSearch algorithm, all the expressions are expanded in advance,
   so simple approximate pattern matching algorithms can be applied for the search.
@@
   If the author of the document does not provide the data, it would be nice if
-  other users can add the ExpandHelp entries.
+  other users can add the {\ES} entries.
   This strategy is very similar to writing a hands-on document for an existing document,
-  but adding ExpandHelp entries is much easier than authoring  a document from scratch.
+  but adding {\ES} entries is much easier than authoring  a document from scratch.
 
@@
 
-Some Unix command line tools have many options and features, and difficult to understand in many cases.
-Many programmers are recently using the git version control system, but the concept of git is difficult, and
+Some Unix command line tools have many options and features that are difficult to remember.
+Many programmers are recently using the git version control system,
+but the concept of git is difficult, and
 the command line options are extremely complicated.
-The total number of git manuals on unix is .....
-
-We created the GitHelp system using {\ES}, so that git users can easily
+The total number of git manuals on unix is xxxxx lines.
+
+We created the {\HL} system using {\ES}, so that git users can easily
 remember command options and use it without perfectly remembering the git commands.
 
-We implemented the HelpLine system
+We implemented the {\HL} system
 with which a user can translate his vague intention in various languages
@@
 
-If HelpLine is installed,
+If {\HL} is installed,
 the user can type a special shortcut key
 (e.g. \texttt{Ctrl-J})
-to invoke HelpLine after typing \sqtt{git RE 2} to see how he can
+to invoke {\HL} after typing \sqtt{git RE 2} to see how he can
 perform the task.
@@
 
-OmniSearch is an implementation of ExpandSearch that runs on Chrome browser.
+OmniSearch is an implementation of {\ES} that runs on Chrome browser.
 The URL window on Chrome is called omnibox,
@@
 
-Figure xxx shows an example {\HF} page that supports finding FAQs
-for PayPay Free market run by Yahoo! Japan.
-We provide the description on the Scrapbox wiki service,
-
-% https://paypayfleamarket.yahoo.co.jp/help/
+Figure \ref{paypayhf} shows an example {\HF} page that supports finding FAQs
+for ``PayPay Free Market'' run by Yahoo! Japan\footnote{
+  \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
+}.
+
+% We provide the description on the Scrapbox wiki service,
 
@@
   \caption{PayPay Freemarket}
+  \label{paypayhf}
   \Description{PayPay}
 \end{figure}
+
+ものすごく問いあわせが減った
 
@@
 
-A flexible search mechanism ``ExpandSearch'' is used in HelpLine.
-%
-The database used in ExpandSearch are provided as a set of data entries
+A flexible search mechanism ``{\ES}'' is used in {\HL}.
+%
+The database used in {\ES} are provided as a set of data entries
 consisting of a regular expression that represents description of the data entry
@@
 
-\paragraph{Applications of ExpandHelp}
+\paragraph{Applications of ExpandSearch}
 

### 2020-10-10 IUI2021/paper.tex
...

@@
 %
-Various techniques have been proposed to solve this vocabulary problem,
+Various techniques have been proposed to solve this vocabulary problem\cite{Furnas},
 but not very successful enough.
@@
 
-\subsection{Query Expansion}
+\subsection*{Query Expansion}
 
@@
 
-The vocabulary problem and the translation problem can be solved
+The vocabulary problem and the translation problem can sometimes be solved
 if the search system have a thesaurus and a translation dictionary.
@@
 For example, 
-if the system knows that removing a file and deleting a file is the same,
+if the system knows that removing a file and deleting a file mean the same thing,
 the system can try to find something using the keyword ``delete'',
@@
 %
-This kind of technique is called ``\textit{Query expansion}'', and simple query
-expansion is possible if proper dictionary is provided.
+Techniques like this are called ``\textit{Query expansion}'',
+and simple query expansion is possible if a good thesaurus is available.
 
@@
 for finding the manual entry.
-
-However, it does not work for finding a document for vague topics.
+More sophisticated query expansion techniques are widely used in various modern
+information retrieval systems.
+
+However, query expansion techniques do not work for finding a document for vague topics.
 For example, if you want to find a document that describes ``how to write a good paper'',
@@
 Similarly, 
-when we want to find a library function of a programming language, query expansion does not work.
+when we want to find a library function of a programming language,
+query expansion sometimes does not work.
 For example, when we want to write a poker game program and
-want to select five cards from the deck, what library should we use?
+want to write a program that select five cards from 52 cards,
+what library should we use?
 you want to selet randomly two items from an array in Ruby,
@@
 It is even more difficult if the user wants to find information that is not easily described with keywords.
-When a user wants to know what the icons on the Mac desktop mean, he might want to to 
-search by saying "What is the symbol with three curved lines
+When a user wants to know the meaning of an icon on the desktop, he might think
+``What is the symbol with curved lines and a circle
 \includegraphics[width=6mm,bb=0 0 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
-on my computer display?
-(folding fan, two black 90-degree arcs above a black circcle)
+at the top of my Mac display?'',
+but he cannot finding the information using these keywords in his brain.
+(folding fan, two black 90-degree arcs above a black circle)
 
@@
 
+We call the combination of these techniques as ``document expansion''.
+
 \begin{enumerate}
@@
 
-  When we want to provide a manual that describes how to delete a file, 
-  we provide a RE like \verb*(delete|remove) (a file|data)*
-  and generate all the text that match this RE.
+  When we want to provide a (flexible?) manual that describes how to delete a file,
+  we expand the original document by
+  providing REs like \verb*(delete|remove) (a file|data)*
+  and generating all the texts that match the REs.
   In this case, we can epand this RE into
@@
   \verb|remove a file|, and
-  \verb|remove data|.
+  \verb|remove data|,
   and use all these strings for the search.
-  Users can find this document by using fleible query like
-  \verb|delete file| or
-  \verb|remove data|.
-  We can add descriptions in other languages, like \verb*(ファイル|データ)を(消す|(消去|削除)する)*
-  A user can use a phrase like ``ファイルを消去する'' to find the manual page.
+  Users can find this document by using various query keywords like
+  \verb|delete|, \verb|remove|, etc.
+  We can add REs in other languages
+  like \verb*(ファイル|データ)を(消す|(消去|削除)する)*.
+  A Japanese user can use a phrase like ``ファイルを消去する'' to find the manual page.
 
@@
 
-  People make spelling errors all the time, and approximate pattern matching algorithm
-  works quite effectively for almost all search activities.
-  Using the ExpandSearch algorithm, all the expressions are expanded in advance,
-  so simple approximate pattern matching algorithms can be applied for the search.
-  For example, a query like ``del dta'' can be used
+  People frequently make spelling errors,
+  and approximate pattern matching algorithms
+  work effectively for almost all search activities.
+  Using the {\ES} algorithm, all the expressions are expanded,
+  and simple approximate pattern matching algorithms work effectively.
+  For example, a query like ``del dta'' will work for
+  finding a document that describes how to ``delete data''.
 
@@
 
-  As we have shown before, one of the big reasons why we fail to find a document is that
+  One of the big reasons why we fail to find a document is that
   the user's search keyword does not exist in the document.
-  Providing entries for {\ES} can solve the problem, but
-
-  If the author of the document does not provide the data, it would be nice if
-  other users can add the {\ES} entries.
-  This strategy is very similar to writing a hands-on document for an existing document,
-  but adding {\ES} entries is much easier than authoring  a document from scratch.
+  If a user can expand the target documents by
+  providing RE entries for {\ES},
+  other users can use {\ES} for finding the documents.
+  %
+  This strategy is similar to creating an external index or
+  writing a hands-on document for an existing document,
+  but adding {\ES} entries is much easier and more flexible than
+  authoring a document from scratch.
 

### 2020-10-10 IUI2021/paper.tex
...

@@
   Although intelligent text search algorithms are widely available
-  these days, documents are still hard to find in many cases. It is
+  these days, searching documents is still difficult in many cases.
+  It is
   usually hard to find useful information in help systems and manual
@@
 \begin{figure}[H]
-  \centering
-  \includegraphics[width=12cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
+  %\centering
+  % \includegraphics[width=7cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
+  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/eaa80e41ddc3d3620fae133007274573.png}
+  % \includegraphics[width=7cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
+  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
+  \par
+  (a) Searching ``remove files'' \hspace{3cm} (b) Searching ``Set clock''
   \caption{Asking the help application on Mac how to remove a file.}
-  \Description{Mac Mac}
+  %\Description{Mac Mac}
 \end{figure}
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=12cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
-  \caption{Mac}
-  \Description{Mac Mac}
-\end{figure}
+% \begin{figure}[H]
+%   \centering
+%   \includegraphics[width=12cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
+%   \caption{Mac}
+%   \Description{Mac Mac}
+% \end{figure}
 
@@
 %
-Techniques like this are called ``\textit{Query expansion}'',
+Techniques like this are called ``\textit{Query expansion}''\footnote{
+  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Query\_expansion}
+},
 and simple query expansion is possible if a good thesaurus is available.
@@
 ``What is the symbol with curved lines and a circle
-\includegraphics[width=6mm,bb=0 0 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
+\includegraphics[width=6mm,bb=-40 30 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
 at the top of my Mac display?'',
@@
 
-% [[ExpandSearchの実例]]
+In this section, we describe how
+document expansion strategy based on {\ES} works in various environments.
+
 %  まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
@@
 
-Some Unix command line tools have many options and features that are difficult to remember.
+Unix command line tools usually have many options and features that are difficult to
+understand and remember.
 Many programmers are recently using the git version control system,

### 2020-10-10 IUI2021/paper.tex
...

@@
 
-% \documentclass[manuscript,anonymous,review]{acmart}
-\documentclass[manuscript,screen,review]{acmart}
+\documentclass[manuscript,anonymous,review]{acmart}
+% \documentclass[manuscript,screen,review]{acmart}
 
@@
 
-The help system of MacOS (Catalina v10.15.5) cannot tell us how to remove a file.
+The standard help system on MacOS (Catalina v10.15.5)
+cannot tell the user how to remove a file (Figure \ref{machelp}(a)).
+%
+It can tell the user how to ``set the clock'', but
+the user has to know that
+``setting the clock'' and ``changing date'' means the same thing (Figure \ref{machelp}(b)).
 
@@
   (a) Searching ``remove files'' \hspace{3cm} (b) Searching ``Set clock''
-  \caption{Asking the help application on Mac how to remove a file.}
+  \caption{Using the standard help application on Mac.}
+  \label{machelp}
   %\Description{Mac Mac}
 \end{figure}
-
-Using the same help application, 
-a user can find how to set the system clock of the computer,
-but the user has to know that
-``setting the clock'' and ``changing date'' means the same thing.
 
@@
 
-We can get this kind of information fairly easily using search systems on the net,
-so many people prefer getting information using search engines rather than
+We can get this kind of information fairly easily using Google and other search engines on the net,
+so many people prefer getting information on the net rather than
 using help systems provided by manufacturers.
@@
 On the other hand,
-finding a less popular information is rather difficult,
-because not enough documents related to the topic is found on the net.
+finding less popular information is more difficult,
+because not enough documents related to the topic exist on the net.
 %
 If there is only one document on the net
-that describes the \texttt{console} feature of a minor system \texttt{xxxxx},
-people cannot find the document using a similar keyword \texttt{dashboard}
-since the document does not contain the word \texttt{dashboard}.
+that describes the \qtt{console} feature of a relatively minor system like \tt{Heroku},
+people cannot find the document using a similar keyword \qtt{dashboard}
+since the documents from \tt{Heroku} does not contain the word \qtt{dashboard}.
 
@@
 
-FAQs (frequently asked questions) provided by service providers are
+FAQs (frequently asked questions) by manufacturers and service providers are
 usually not considered useful
-because the terms used by the people on the service are usually
-different from the keywords that user can imagine.
+because the words used in the documents are
+often different from the keywords that user can imagine.
 
@@
 
-Even finding the users' old documents can be sometimes difficult,
+Even finding the users' old memos can be sometimes difficult,
 because people might use different keywords for the same thing case by case.
@@
 %
-Various techniques have been proposed to solve this vocabulary problem\cite{Furnas},
+Various techniques have been proposed to solve this vocabulary problem\cite{Furnas:1987:VPH:32206.32212},
 but not very successful enough.
@@
 manual of the system is written in French,
-he has to translate the term ``delete'' and ``file'' into French
+he has to \textit{translate} the term ``delete'' and ``file'' into French
 before the search.
@@
 
-The vocabulary problem and the translation problem can sometimes be solved
+The vocabulary problem and the translation problem can partially be solved
 if the search system have a thesaurus and a translation dictionary.
@@
 },
-and simple query expansion is possible if a good thesaurus is available.
+and simple query expansion is effective if a good thesaurus is available.
 
@@
 However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
-unless the expander knows the contents.
+unless the expander understands the intension of the user.
 
@@
 
-Similarly, 
-when we want to find a library function of a programming language,
-query expansion sometimes does not work.
-For example, when we want to write a poker game program and
-want to write a program that select five cards from 52 cards,
-what library should we use?
-you want to selet randomly two items from an array in Ruby,
-you can use the \texttt{sample()} method.
-However, ``randomly selecting items'' and \texttt{sample} are so different, it is very hard for users to
-find the method unless the manual contains words like ``randomly select''.
-
+% ライブラリ関数 (やめる)
 % 「配列からランダムに要素をふたつ取得」 = `a.sample(2)`
@@
 
-It is even more difficult if the user wants to find information that is not easily described with keywords.
-When a user wants to know the meaning of an icon on the desktop, he might think
-``What is the symbol with curved lines and a circle
-\includegraphics[width=6mm,bb=-40 30 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
-at the top of my Mac display?'',
-but he cannot finding the information using these keywords in his brain.
-(folding fan, two black 90-degree arcs above a black circle)
+% Similarly, 
+% when we want to find a library function of a programming language,
+% query expansion sometimes does not work.
+% For example, when we want to write a poker game program and
+% want to write a program that select five cards from 52 cards,
+% what library should we use?
+% you want to selet randomly two items from an array in Ruby,
+% you can use the \texttt{sample()} method.
+% However, ``randomly selecting items'' and \texttt{sample} are so different, it is very hard for users to
+% find the method unless the manual contains words like ``randomly select''.
 
@@
 % [[原文を拡張する感じにして、簡潔なインタフェースを用意して任意のキーワードを使えるのが良い]]
+
+It is even more difficult if the user wants to find information that is not easily described with keywords.
+When a user wants to know the meaning of an icon on the computer desktop, he might want to say
+``What is the symbol with curved lines and a circle
+\includegraphics[width=6mm,bb=-40 30 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
+at the top of my Mac display?'',
+but he cannot find the information using such keywords in his brain.
+% (folding fan, two black 90-degree arcs above a black circle)
 
@@
 we propose the combination of three techniques described below.
-
-We call the combination of these techniques as ``document expansion''.
+%
+We call the combination of these techniques as ``\textit{document expansion}''.
 
@@
 
-  When we want to provide a (flexible?) manual that describes how to delete a file,
+  When we want to publish a easy-to-find manual that describes how to delete a file,
   we expand the original document by
-  providing REs like \verb*(delete|remove) (a file|data)*
+  providing REs like \qtt{(delete|remove) (a file|data)}
   and generating all the texts that match the REs.
   In this case, we can epand this RE into
-  \verb|delete a file|,
-  \verb|delete data|,
-  \verb|remove a file|, and
-  \verb|remove data|,
+  \qtt{delete a file},
+  \qtt{delete data},
+  \qtt{remove a file}, and
+  \qtt{remove data},
   and use all these strings for the search.
   Users can find this document by using various query keywords like
-  \verb|delete|, \verb|remove|, etc.
+  \qtt{delete}, \qtt{remove}, etc.
   We can add REs in other languages
-  like \verb*(ファイル|データ)を(消す|(消去|削除)する)*.
+  like \qtt{(ファイル|データ)を(消す|(消去|削除)する)}.
   A Japanese user can use a phrase like ``ファイルを消去する'' to find the manual page.
@@
 
-  People frequently make spelling errors,
-  and approximate pattern matching algorithms
+  Since people frequently make spelling errors,
+  approximate pattern matching algorithms
   work effectively for almost all search activities.
-  Using the {\ES} algorithm, all the expressions are expanded,
-  and simple approximate pattern matching algorithms work effectively.
-  For example, a query like ``del dta'' will work for
+  After getting all the expresssions expanded by the {\ES} algorithm,
+  simple approximate pattern matching algorithms work effectively.
+  For example, a query string like \qtt{del dta} will work for
   finding a document that describes how to ``delete data''.
@@
   If a user can expand the target documents by
-  providing RE entries for {\ES},
+  providing RE entries for {\ES} and share them,
   other users can use {\ES} for finding the documents.
@@
 
+In the next section, we describe how
+document expansion strategy based on {\ES} works in various environments.
+
 \section{Examples}
-
-In this section, we describe how
-document expansion strategy based on {\ES} works in various environments.
 
@@
 understand and remember.
-Many programmers are recently using the git version control system,
-but the concept of git is difficult, and
-the command line options are extremely complicated.
-The total number of git manuals on unix is xxxxx lines.
-
-We created the {\HL} system using {\ES}, so that git users can easily
-remember command options and use it without perfectly remembering the git commands.
+For example, many programmers are recently using a version controll system
+``git''\footnote{
+  \ssf{https:{\slash}{\slash}git-scm.com{\slash}}
+},
+but the concept of git is difficult and the command line options are extremely complicated.
+The total number of git manuals pages is bigger than 70,000.
+
+To solve the difficulty of using commands,
+we created the {\HL} system using {\ES}, so that users of git and other complicated systems can
+easily remember command options and use it without remembering the details of the commands.
 
@@
 with which a user can translate his vague intention in various languages
-into a complete {\GIT} command
-using the {\ES} framework.
+into a complete command line using the {\ES} framework.
 
@@
 
-We assume that the user uses \tt{bash} for his software
-development activities.
-% 
-When a user wants to compare the latest \stt{README.md} file
+We assume that the user uses \tt{bash} for his software development activities.
+% 
+When a user wants to compare the latest \sqtt{README.md} file
 with the same file from 2 versions before,
@@
 
-\begin{figure}[h]
-  \vbox{
+% \begin{figure}[h]
+%   \vbox{
+%     \begin{verbatim}
+%       $ git diff HEAD^^ README.md
+%       $
+%     \end{verbatim}
+%   }
+%   \caption{Invoking \stt{git diff}.}
+%   \label{gitdiff}
+% \end{figure}
+
+\begin{quote}
 \begin{verbatim}
@@
 \end{verbatim}
-  }
-  \caption{Invoking \stt{git diff}.}
-  \label{gitdiff}
-\end{figure}
+\end{quote}
 
@@
 specifies a file included in the older commit,
-and the command in figure \ref{gitdiff} only compares the
-\stt{README.md} with the file included in an old commit, where
-\stt{README.md} might not have changed since then.
+and the command compares the
+\sqtt{README.md} with the file included in an old commit, where
+\sqtt{README.md} might not have changed since then.
 
@@
 
-\begin{figure}[h]
-  \includegraphics[width=9cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
-  \caption{Invoking {\HL} after typing \stt{git read 2}.}
+\begin{figure}[H]
+  \includegraphics[width=8cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
+  \caption{Invoking {\HL} after typing \sqtt{git read 2}.}
   \label{example1}
@@
 and if the user thinks that's what he wants to do,
-he can select the entry by typing arrow keys and the enter key.
-Then the user's input string is replaced by the right command string
+he can select the entry by typing arrow keys.
+After typing the enter key for confirmation,
+the user's input string is replaced by the right command string
 that satisfies the user's need.
@@
 This means that the user can use the same string \sqtt{git RE 2}
-for getting the information of \stt{README.md} file of the day before yesterday.
+for getting the information of \sqtt{README.md} file of the day before yesterday.
 The generated argument
 ``{\smallfont\verb|@{2 days ago}|}'',
-may not be familiar to most {\GIT} users,
+may not be familiar to most {\GIT} users\footnote{
+  The authors asked more than 10 experienced git users if they know that option,
+  but nobody knew it.
+},
 but users can perform this task only by giving \sqtt{RE} and \sqtt{2}
@@
 approximate pattern matching is automatically performed, and
-entries related to \stt{README.md} file are listed because
+entries related to \sqtt{README.md} file are listed because
 \sqtt{reed} matches \sqtt{README.md} with one error.
 
-\begin{figure}[h]
-  \includegraphics[width=9cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
+\begin{figure}[H]
+  \includegraphics[width=8cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
   \caption{Invoking {\HL} after typing \stt{git sh reed 3}.}
@@
 
-\begin{figure}[t]
-  \includegraphics[width=12cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
+\begin{figure}[H]
+  \includegraphics[width=8cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
   \caption{Invoking {\HL} in Japanese environment.}
@@
 \raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{../../GitHelp/paper/figures/info-xxl.png}}
-button and see the Wiki page shown in Figure \ref{scrapboxpage}.
+button and see the wiki page\footnote{
+  A wiki system {\SB} (\ssf{https:{\slash}{\slash}Scrapbox.io{\slash}product{\slash}}) is used for the data sharing.
+} shown in Figure \ref{scrapboxpage}.
 The user can edit the page if he wants to add information or finds an error.
@@
 
-\begin{figure}[t]
+\begin{figure}[H]
   \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{../../GitHelp/paper/figures/scrapbox3.png}}
@@
 
-\subsection{OmniSearch}
-
-OmniSearch is an implementation of {\ES} that runs on Chrome browser.
-The URL window on Chrome is called omnibox,
+Since the REs for expanding git manuals are written on wiki pages,
+any members of the wiki project can edit the data and share it among other users.
+
+% \subsection{OmniSearch}
+% 
+% OmniSearch is an implementation of {\ES} that runs on Chrome browser.
+% The URL window on Chrome is called omnibox,
 
@@
   \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
-}.
-
-% We provide the description on the Scrapbox wiki service,
+} and ``Siroca'', a consumer electronics company.
 
@@
   \centering
-  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
+  % \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
+  \includegraphics[width=7cm,bb=0 0 1982 1536]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
+  \includegraphics[width=7cm,bb=0 0 1672 1472]{figures/6b491f2701af7193030e332686733568.png}
   \caption{PayPay Freemarket}
   \label{paypayhf}
-  \Description{PayPay}
-\end{figure}
-
-ものすごく問いあわせが減った
+  %\Description{PayPay}
+\end{figure}
+
+After the introduction of ExpandSearch-based FAQ services,
+the number of phone calls to the customer support center of these companies have
+dramatically reduced, as much as 60\%.
+%
+The ``hit rate'' at which users could find the information they need was 98\%.
 
@@
 
-%\bibliographystyle{SIGCHI-Reference-Format}
-%\bibliography{paper}
+\newpage
+
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{paper}
 

### 2020-10-10 IUI2021/paper.tex
...

@@
 We have been applying ExpahdSearch for various customer support services on existing Web services.
-The help system based on {\ES} is called {\HF}, and
-
-{\HF} is a FAQ engine that supports users who do not have enough vocabulary for the Web services they want to use.
+The system is called {\HF}\footnote{
+  \ssf{https:{\slash}{\slash}helpfeel.com{\slash}}
+}, and
+it supports users who do not have enough vocabulary for the Web services they want to use.
 
@@
 the number of phone calls to the customer support center of these companies have
-dramatically reduced, as much as 60\%.
+dropped to 40\%.
 %
@@
 
-\begin{verbatim}
-[[実装]]
- ExpandHelpのアルゴリズム
-  正規表現の拡張とパラメタ代入
- HelpLineの実装
-  omniboxを利用するとか
-\end{verbatim}
+% [[実装]]
+%  ExpandHelpのアルゴリズム
+%   正規表現の拡張とパラメタ代入
+%  HelpLineの実装
+%   omniboxを利用するとか
 
@@
 
-Special symbols like \stt{\#\{files\}} in the description part is expanded to
-the list of filenames like \stt{README.md|index.html}.
+Special symbols like \sqtt{\#\{files\}} in the description part is expanded to
+the list of filenames like \sqtt{README.md|index.html}.
 The first regular expression, the description part,
@@
 \end{quote}
-
 can be used for Japanese {\GIT} users.
@@
 
-Finding appropriate entries from the (possibly huge) help document space is
+Finding appropriate entries from the
+% (possibly huge)
+help document space is
 performed in two steps.
@@
 Starting at the start node
-(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{../../GitHelp/paper/figures/startnode.pdf}})
+\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{../../GitHelp/paper/figures/startnode.pdf}}
 in Figure \ref{statemachine1},

### 2020-10-10 IUI2021/paper.tex
...

@@
 \long\def\tt#1{\texttt{#1}}
-\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
+\long\def\stt#1{\texttt{\fontsize{8pt}{0pt}\selectfont{#1}}}
 \long\def\sf#1{\textsf{#1}}
-\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
+\long\def\ssf#1{\textsf{\fontsize{8pt}{0pt}\selectfont{#1}}}
 \long\def\qtt#1{``\tt{#1}''}   % quote tt
@@
 \long\def\qit#1{``\textit{#1}''}
-\long\def\smallfont{\fontsize{9pt}{0pt}\selectfont}
+\long\def\smallfont{\fontsize{8pt}{0pt}\selectfont}
 
@@
 by asking in user forums like StackOverflow\footnote{
-  \textsf{https://stackoverflow.com/}
+  \ssf{https:{\slash}{\slash}stackoverflow.com{\slash}}
 }.
@@
 
-\begin{verbatim}
-    検索システムを選んでから検索キーワードを入力するのに慣れてしまっている
-  この必要がないことを知ると驚きがある
- 検索されやすいように工夫するとか馬鹿げてると
-思うかもしれないか、ググって出なきゃ無いのと同じだということを考えると、
-ある程度工夫することは意味があるし、自分が後でさがすときにも役に立つわけである
-  ゲームのように記述を増やす工夫もできるかもしれない
-  タイトルに迷ったら両方書くみたいな
- どこにある情報でもひとつのインタフェースでみつかるのは強烈に嬉しい
-
-[[説得ポイント]]
- ExpandHelp
-  自分が入力したキーワードが検索結果に出現する嬉しさ
- 検索方法の統合
- ヘルプシステムの実績
-
-[[関連システム / 参考文献]]
- 普通の[https://en.wikipedia.org/wiki/Query_expansion クエリ拡張]
- Relevance Feedback
-  検索パタンを増やすことに効果があるといえる
- [https://scrapbox.io/UIPedia/George_Furnas:_The_vocabulary_problem_in_human-system_communication Vocabulary problem]
- [文芸的プログラミング]
-  ExpandHelp記述は文芸的プログラミングの一種だと思えばいい
-  冗長な感じで書くといい
- [/Rubytips] の実例
-
-日本語を入力すると英語のWikipediaがみつかることもある
- これはたぶん原文を翻訳したものを検索対象にしている
- これもDocument Expansionといえる
-
-\end{verbatim}
-
-\paragraph{Applications of ExpandSearch}
+%     検索システムを選んでから検索キーワードを入力するのに慣れてしまっている
+%   この必要がないことを知ると驚きがある
+%  検索されやすいように工夫するとか馬鹿げてると
+% 思うかもしれないか、ググって出なきゃ無いのと同じだということを考えると、
+% ある程度工夫することは意味があるし、自分が後でさがすときにも役に立つわけである
+%   ゲームのように記述を増やす工夫もできるかもしれない
+%   タイトルに迷ったら両方書くみたいな
+%  どこにある情報でもひとつのインタフェースでみつかるのは強烈に嬉しい
+% 
+% [[説得ポイント]]
+%  ExpandHelp
+%   自分が入力したキーワードが検索結果に出現する嬉しさ
+%  検索方法の統合
+%  ヘルプシステムの実績
+% 
+% [[関連システム / 参考文献]]
+%  普通の[https://en.wikipedia.org/wiki/Query_expansion クエリ拡張]
+%  Relevance Feedback
+%   検索パタンを増やすことに効果があるといえる
+%  [https://scrapbox.io/UIPedia/George_Furnas:_The_vocabulary_problem_in_human-system_communication Vocabulary problem]
+%  [文芸的プログラミング]
+%   ExpandHelp記述は文芸的プログラミングの一種だと思えばいい
+%   冗長な感じで書くといい
+%  [/Rubytips] の実例
+% 
+% 日本語を入力すると英語のWikipediaがみつかることもある
+%  これはたぶん原文を翻訳したものを検索対象にしている
+%  これもDocument Expansionといえる
+
+\subsection*{Other applications of ExpandSearch}
 
@@
   %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
-  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
+  \centerline{\includegraphics[width=7cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
   \caption{Using {\ES} in the menu bar of MacOS.}
@@
   %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
-  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
+  \centerline{\includegraphics[width=7cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
   \caption{Using {\ES} in the menu bar of MacOS.}
@@
 
-\paragraph{Order of command and arguments}
+\subsection*{Order of command and arguments}
 
@@
 
-\paragraph{Usage of regular expressions}
+\subsection*{Usage of regular expressions}
 

### 2020-10-10 IUI2021/paper.tex
...

@@
 %
-%
+% IUI2021 HelpLine (GitHelp)
 %
@@
 \acmConference[IUI '21]{IUI '21: ACM Conference}
-  {June 03--05, 2020}{Somewhere, Italy}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
+  {April 13--17, 2021}{College Station, AZ}
+\acmBooktitle{IUI '21: ACM Symposium on Intelligent User Interface,
+  April 13--17, 2021, College Station, AZ}
 \acmPrice{15.00}
@@
   <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+    <concept_id>10002951.10003317.10003338.10010403</concept_id>
+    <concept_desc>Information systems~Novelty in information retrieval</concept_desc>
     <concept_significance>500</concept_significance>
@@
   <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+    <concept_id>10003120.10003121.10003124.10010862</concept_id>
+    <concept_desc>Human-centered computing~Command line interfaces</concept_desc>
+    <concept_significance>500</concept_significance>
   </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Information systems~Novelty in information retrieval}
+\ccsdesc[500]{Human-centered computing~Command line interfaces}
+
+% \ccsdesc[500]{Computer systems organization~Embedded systems}
+% \ccsdesc[300]{Computer systems organization~Redundancy}
+% \ccsdesc{Computer systems organization~Robotics}
+% \ccsdesc[100]{Networks~Network reliability}
 
@@
 \raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{../../GitHelp/paper/figures/info-xxl.png}}
-button and see the wiki page\footnote{
-  A wiki system {\SB} (\ssf{https:{\slash}{\slash}Scrapbox.io{\slash}product{\slash}}) is used for the data sharing.
-} shown in Figure \ref{scrapboxpage}.
+button and see the {\SB}\footnote{
+  \ssf{https:{\slash}{\slash}Scrapbox.io{\slash}product{\slash}}
+} wiki page shown in Figure \ref{scrapboxpage}.
 The user can edit the page if he wants to add information or finds an error.
@@
 
+% \includegraphics[width=7cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
+% \includegraphics[width=7cm,bb=-50 0 950 800]{figures/eaa80e41ddc3d3620fae133007274573.png}
+
 \begin{figure}[H]
@@
   % \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
-  \includegraphics[width=7cm,bb=0 0 1982 1536]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
-  \includegraphics[width=7cm,bb=0 0 1672 1472]{figures/6b491f2701af7193030e332686733568.png}
-  \caption{PayPay Freemarket}
+  % \includegraphics[width=9cm,bb=0 0 1982 1536]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
+  \includegraphics[width=7cm,bb=-200 0 1400 1400]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
+  % \includegraphics[width=9cm,bb=0 0 1672 1472]{figures/6b491f2701af7193030e332686733568.png}
+  \includegraphics[width=7cm,bb=-200 0 1200 1300]{figures/6b491f2701af7193030e332686733568.png}
+  \caption{FAQ services based on Helpfeel.} 
   \label{paypayhf}
@@
 
-The data used in {\HL} are represented as ``{\SB}'' documents
+The data used in {\HL} are represented as {\SB} documents
 shown in Figure \ref{scrapboxpage}.
@@
 on Web browsers just like using text editors.
-
-% \begin{figure}[htb]
-% \begin{verbatim}
-% \end{verbatim}
-% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{../../GitHelp/paper/figures/scrapbox1.png}}
-% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{../../GitHelp/paper/figures/scrapbox1.png}}
-% \caption{A {\SB} page for \tt{git diff}.}
-% \label{xxxxx}
-% \end{figure}
 
@@
 people are using them every day for entering texts in their mother language.
-Figure \ref{gyaim} shows an example of a Japanese IM.
-
-\begin{figure}[H]
-  % \includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}
-  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}}
-  \caption{An IM for Japanese text input.}
-  \label{gyaim}
-\end{figure}
+
+% Figure \ref{gyaim} shows an example of a Japanese IM.
+% 
+% \begin{figure}[H]
+%   % \includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}
+%   \centerline{\includegraphics[width=7cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}}
+%   \caption{An IM for Japanese text input.}
+%   \label{gyaim}
+% \end{figure}
 
@@
 
-\subsection*{Other applications of ExpandSearch}
-
-Since the translation mechanism of {\ES} is simple and flexible,
-it can be used for a wide range of application domains where
-intelligent help is required.
-{\ES} is actually used as the help page for
-one of our Web services, hoping that
-novice users can easily find the feature they need.
-When a user submits a query that includes vocabularies
-not in the {\ES} document,
-we are able to add them to the {\SB} database easily.
-
-Figure \ref{mac1} and Figure \ref{mac2} shows how
-{\ES} can be used as a launcher for MacOS.
-Like {\HL}, users can execute concrete commands only by
-showing small fragments of their intentions to the system.
-
-\begin{figure}[h]
-  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
-  \centerline{\includegraphics[width=7cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
-  \caption{Using {\ES} in the menu bar of MacOS.}
-  \label{mac1}
-\end{figure}
-
-\begin{figure}[h]
-  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
-  \centerline{\includegraphics[width=7cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
-  \caption{Using {\ES} in the menu bar of MacOS.}
-  \label{mac2}
-\end{figure}
+% \subsection*{Other applications of ExpandSearch}
+% 
+% Since the translation mechanism of {\ES} is simple and flexible,
+% it can be used for a wide range of application domains where
+% intelligent help is required.
+% {\ES} is actually used as the help page for
+% one of our Web services, hoping that
+% novice users can easily find the feature they need.
+% When a user submits a query that includes vocabularies
+% not in the {\ES} document,
+% we are able to add them to the {\SB} database easily.
+% 
+% Figure \ref{mac1} and Figure \ref{mac2} shows how
+% {\ES} can be used as a launcher for MacOS.
+% Like {\HL}, users can execute concrete commands only by
+% showing small fragments of their intentions to the system.
+% 
+% \begin{figure}[h]
+%   %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
+%   \centerline{\includegraphics[width=7cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
+%   \caption{Using {\ES} in the menu bar of MacOS.}
+%   \label{mac1}
+% \end{figure}
+% 
+% \begin{figure}[h]
+%   %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
+%   \centerline{\includegraphics[width=7cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
+%   \caption{Using {\ES} in the menu bar of MacOS.}
+%   \label{mac2}
+% \end{figure}
 

### 2020-10-10 IUI2021/paper.tex
Grammarlyを通した

@@
 
-% \ccsdesc[500]{Computer systems organization~Embedded systems}
-% \ccsdesc[300]{Computer systems organization~Redundancy}
-% \ccsdesc{Computer systems organization~Robotics}
-% \ccsdesc[100]{Networks~Network reliability}
-
 %%
@@
 
-People are frequently searching information using keywords on Google
+People are frequently searching for information using keywords on Google
 and other systems.
-But keyword search is still not an easy task,
-because it is fundamentally difficulto to find appropriate information
-that does not contain the keyword given by the user.
+But keyword search is still not an easy task because it is
+fundamentally difficult to find appropriate information that does not
+contain the user's keywords.
 
@@
 
-We can get this kind of information fairly easily using Google and other search engines on the net,
-so many people prefer getting information on the net rather than
-using help systems provided by manufacturers.
-
-We can find information on Google because there are tremendous information
-that describe how to ``remove a file'' on Mac.
-If there are documens that contain ``remove'', ``file'', and ``Mac'',
+We can get this kind of information fairly easily using Google and
+other search engines on the net, so many people prefer getting
+information on the net rather than using manufacturers' help systems.
+
+We can find information on Google because there is tremendous information
+that describes how to ``remove a file'' on Mac.
+If there are documents that contain ``remove,'' ``file,'' and ``Mac'',
 finding such documents are not difficult.
@@
 because the words used in the documents are
-often different from the keywords that user can imagine.
+often different from the keywords that users can imagine.
 
@@
 because people might use different keywords for the same thing case by case.
-He might try to find a file related to ``IUI'' and fail, because he used
+He might try to find a file related to ``IUI'' and fail because he used
 the term ``intelligent user interface'' for the file name.
@@
 
-Finding documents are even more difficult when
+Finding documents is even more difficult when
 the user's mother language is different from the language used in the document.
@@
 Non-English speakers are always having trouble
-translating the word in their brain into English words
-before searching information, because important information are
-usually provided in English.
+translating the word in their brains into English words
+before searching for information, because important information is
+provided in English in many cases.
 
@@
 The vocabulary problem and the translation problem can partially be solved
-if the search system have a thesaurus and a translation dictionary.
+if the search system has a thesaurus and a translation dictionary.
 %
 For example, 
-if the system knows that removing a file and deleting a file mean the same thing,
-the system can try to find something using the keyword ``delete'',
-even when the user specified the keyword ``remove''.
+if the system knows that removing a file and deleting a file means the same thing,
+the system can try to find something using the keyword ``delete''
+even when the user specified the keyword ``remove.''
 %
@@
 
-Query expansion is effective when simple substitution of keywords are satisfactory enough.
+Query expansion is effective when a simple substitution of keywords is satisfactory enough.
 In the previous example, using the keyword ``delete'' in addition to ``remove'' works
@@
 However, query expansion techniques do not work for finding a document for vague topics.
-For example, if you want to find a document that describes ``how to write a good paper'',
-you will have little chance finding a document related to the topic.
-Maybe it would be better to use keywords like ``how to persuade reviewers''.
-However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
-unless the expander understands the intension of the user.
+For example, if you want to find a document that describes ``how to write a good paper,''
+you will have little chance of finding a document related to the topic.
+Maybe it would be better to use keywords like ``how to persuade reviewers.''
+However, expanding a phrase like ``write a good paper'' to ``persuade reviewers'' is impossible,
+unless the expander understands the intention of the user.
 
@@
 
-  When we want to publish a easy-to-find manual that describes how to delete a file,
+  When we want to publish an easy-to-find manual that describes how to delete a file,
   we expand the original document by
@@
   and generating all the texts that match the REs.
-  In this case, we can epand this RE into
+  In this case, we can expand this RE into
   \qtt{delete a file},
@@
   work effectively for almost all search activities.
-  After getting all the expresssions expanded by the {\ES} algorithm,
+  After getting all the expressions expanded by the {\ES} algorithm,
   simple approximate pattern matching algorithms work effectively.
   For example, a query string like \qtt{del dta} will work for
-  finding a document that describes how to ``delete data''.
+  finding a document that describes how to ``delete data.''
 
@@
 In the next section, we describe how
-document expansion strategy based on {\ES} works in various environments.
+document-expansion strategy based on {\ES} works in various environments.
 
@@
 
-Unix command line tools usually have many options and features that are difficult to
+Unix command-line tools usually have many options and features that are difficult to
 understand and remember.
-For example, many programmers are recently using a version controll system
+For example, many programmers are recently using a version control system
 ``git''\footnote{
@@
 },
-but the concept of git is difficult and the command line options are extremely complicated.
+but the concept of git is difficult, and the command-line options are extremely complicated.
 The total number of git manuals pages is bigger than 70,000.
@@
 Figure \ref{paypayhf} shows an example {\HF} page that supports finding FAQs
-for ``PayPay Free Market'' run by Yahoo! Japan\footnote{
+for ``PayPay Free Market''\footnote{
   \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
-} and ``Siroca'', a consumer electronics company.
+} run by Yahoo! Japan and ``Siroca''\footnote{
+  \ssf{https:{\slash}{\slash}www.siroca.co.jp{\slash}support{\slash}}
+}, a consumer electronics company.
 
@@
 
-After the introduction of ExpandSearch-based FAQ services,
-the number of phone calls to the customer support center of these companies have
+After introducing ExpandSearch-based FAQ services,
+the number of phone calls to the customer support center of these companies has
 dropped to 40\%.
@@
 
-A flexible search mechanism ``{\ES}'' is used in {\HL}.
-%
-The database used in {\ES} are provided as a set of data entries
-consisting of a regular expression that represents description of the data entry
+A flexible search mechanism, ``{\ES}'', is used in {\HL}.
+%
+The database used in {\ES} is provided as a set of data entries
+consisting of a regular expression that represents a description of the data entry
 and a corresponding command pattern string.
 A description string is used to produce natural language texts
-that are easily understandable by users,
-while command patterns represents the generated command string
+easily understandable by users,
+while command patterns represent the generated command string
 corresponding to the description.
@@
 Second, all the description strings are generated by expanding the regular expression
-into a tree, and filter the generated strings by the pattern specified by the user.
+into a tree, and filtering the generated strings by the user's pattern.
 Efficient pattern matching is performed every time a new description text is generated,
@@
 Using the state transition diagram shown in Figure \ref{statemachine1},
-{\ES} generates all the strings represented in the regular expressions,
+{\ES} generates all the strings represented in the regular expressions
 and filter them by the pattern provided by the user.
@@
 ``Generate-and-test''\footnote{
-  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
+  \ssf{http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
 }
@@
 On text editors and Unix shells,
-``text completion'' feature has been available for a long time.
+``text completion'' has been available for a long time.
 %
@@
 
-Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
-helps {\GIT} users by
+Gitsome\footnote{
+  \ssf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}
+} helps {\GIT} users by
 dynamically showing possible arguments and related manuals on the Unix shell,
@@
 
-We proposed the ``translation paradigm'' for bridging the gap between
+We proposed the ``document expansion'' paradigm for
+flexible text search and
+the ``translation paradigm'' for bridging the gap between
 users' intention and actual operations.
 %
-We have introduced a general-purpose flexible framework {\ES}
+We have introduced a general-purpose flexible framework, {\ES},
 that can translate fragments of user's vague intentions into
-concrete command strings required to control computers and
-other complex artifacts.
+concrete strings required to search for information or
+control computers and other complex artifacts.
 We showed the principles and applications of {\ES} by using it
-for {\HL}, a help system for supporting {\GIT} users
+for {\HL}, a help system for supporting command-line users
 based on the shared database that any user can edit to share
@@
 %
-{\ES} framework is useful for any kind of systems that need
-some kind of user support, and we are planning to use it
-for various applications and Web services in the future.
+{\ES} framework is useful for any systems that need
+some user support, and we are planning to use it
+for a wider range of applications and Web services in the future.
 

### 2021-07-23 omnibox/background.js
'/ ' で起動される方法の説明を追加

@@ -2,6 +2,12 @@
 //  https://developer.chrome.com/extensions/omnibox のサンプルをもとにしている
 //
 
+//
+// https://developer.mozilla.org/ja/docs/Mozilla/Add-ons/WebExtensions/API/omnibox
+// manifest.jsonに "omnibox": { "keyword" : "/" } というエントリを書いておくと、
+// '/' と' 'を押したとき onInputChanged でキー入力を取得できるようになる
+//
+
 'use strict';
 
 const Asearch = require("asearch") // browserifyで展開
